---
name: Dominique
surname: Makowski
profilepic: "./img/profile.png"
position: "Research Fellow"
qualifications: "PhD"
address: "Nanyang Technological University, Singapore"
# phone: +1 22 3333 4444
www: dominiquemakowski.github.io
email: "dom.makowski@gmail.com"
twitter: Dom_Makowski
github: DominiqueMakowski
# linkedin: dominiquemakowski
# orcid: "0000-0001-5375-9967"
aboutme: |
  \RaggedRight Trained as neuropsychologist, I am currently a postdoc in Singapore researching aspects of reality bending (e.g., neuroscience of deception, perception of fake news, altered states of consciousness), the role of the body and emotions in cognition (e.g., emotion regulation and interoception), and methodology (statistics, programming, and neurophysiological techniques).
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "1976D2"
output:
  vitae::awesomecv:
    page_total: true
    keep_md: true
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(ggplot2)

link <- function(txt, url, color = "1976D2") {
  paste0("\\href{", url, "}{\\color[HTML]{", color, "}{", txt, "}}")
}

short <- FALSE
```

# Current Position

```{r CurrentEmployment}
data <- tibble(
  what = "Presidential Postdoctoral Fellow",
  when = "2020 - Present",
  with = "Clinical Brain Lab, Nanyang Technological University (NTU)",
  where = "Singapore",
  details = c(
    paste(
      "The",
      link("NTU Presidential Postdoc award", "https://www.ntu.edu.sg/research/research-careers/presidential-postdoctoral-fellowship-(ppf)"),
      "funded two years of postdoc to develop my own research direction"
    ),
    paste(
      "The team I lead (see ",
       link("Reality Bending", "https://realitybending.github.io/"),
      ") works on the neurocognitive and affective processes underlying the beliefs in fake vs. real stimuli (fake news, fiction, ...)"
    ),
    paste(
      "Reference:",
      link("Pr Annabel Chen", "https://www.clinicalbrain.org/author/annabel-chen/")
    )
  )
)

detailed_entries(data, with, when, what, where, details, .protect = FALSE)
```

\footnotesize

The NTU "presidential postdoc fellowship" is a competitive grant meant as an intermediate step between postdoc and faculty. While integrated within a larger lab (the [Clinical Brain Lab](https://www.clinicalbrain.org/), directed by Prof Annabel Chen), I am pursuing my own research track on the perception of reality, managing my team (3 research assistants, and several undergrad students) and research funding ($ 200k). I am involved in all the research and administrative aspects of the project (writing IRBs, project budgeting, experiment creations, data collection, analysis, manuscript writing, ...).

On top of the mentoring and teaching done in the context of the lab, I am also involved in university lectures (e.g., statistics for NTU students), research-oriented workshops (for instance, I will be introducing our software *NeuroKit* at the OHBM conference this summer), and other trainings (I have been appointed by the University of Zurich to give a 3 days course on Python to their PhD students).

\normalsize


# Education

```{r Education}
data <- rbind(tibble(
  what = "Doctor of Philosophy (PhD) - Psychology",
  when = "2014 - 18",
  with = "Université de Paris",
  where = "France",
  details = paste0(
    "Thesis: Cognitive Neuropsychology of Implicit Emotion Regulation through Fictional Reappraisal (supervised by ",
    link("Pr Serge Nicolas", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Serge-Nicolas"),
    " \\& ",
    link("Pr Pascale Piolino", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Pascale-Piolino"),
    ")"
  )
), tibble(
  what = "Certified Psychotherapist - Cognitive Behavioural Therapy (CBT)",
  when = "2014 - 17",
  with = "French Association for Cognitive Behavioural Therapy (AFTCC)",
  where = "France",
  details = c(
    "Thesis: Cognitive Behavioural Therapy for two Patients: One suffering from Motivation Disorder associated with Dysthymia and the other from Social Anxiety (supervised by Sophie Kindynis)"
  )
), tibble(
  what = "Master of Science (MSc) - Clinical Neuropsychology and Cognitive Psychology",
  when = "2012 - 14",
  with = "Université de Paris",
  where = "France",
  details = c(
    paste0("Second year thesis: How the Study of Emotions in Schizophrenia enlight the Paradox of Fiction (supervised by ", link("Pr Pascale Piolino", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Pascale-Piolino"), ")"),
    paste0("First year thesis: The Cognitive Development of the Aesthetic Judgement in Children and Adults (supervised by ", link("Pr Sandrine Rossi", "https://www.researchgate.net/profile/Sandrine-Rossi"), ")")
  )
), tibble(
  what = "Bachelor of Arts (BA) - Psychology",
  when = "2009 - 12",
  with = "Université de Paris",
  where = "France",
  details = NA
))

if (short) {
  data <- data[1:3, ]
  data$details <- NA
}

detailed_entries(data, with, when, what, where, details, .protect = FALSE)
```


# Experience

## Research

```{r ExperienceResearch}
data <- rbind(
tibble(
  Position = "Research Fellow",
  Date = "2019 - 20",
  Institution = "Clinical Brain Lab, Nanyang Technological University (NTU)",
  Where = "Singapore",
  Activity = paste0(
    "First postdoc position, working on a project funded by the ministry of defence about the neurocognitive correlates of deception. Responsible for studies design and completion, data analysis, publications and co-supervision of one PhD student, two research assistants and several graduate and undergraduate students (reference: ",
    link("Pr Annabel Chen", "https://www.clinicalbrain.org/author/annabel-chen/"),
    ")."
  )
)
, tibble(
  Position = "Research Assistant",
  Date = "2012",
  Institution = "Developmental Psychology Lab (LaPsyDé), Université de Paris",
  Where = "Paris, France",
  Activity = paste0(
    "Data collection for a study (",
    link("Borst, 2016", "http://psycnet.apa.org/journals/emo/13/5/811/"),
    ") on emotions and mental rotation (reference: ", link("Pr Grégoire Borst", "https://www.lapsyde.com/gregoire-borst"),
    ")."
  )
)
, tibble(
  Position = "Research Assistant",
  Date = "2011",
  Institution = "Memory \\& Cognition Lab (LMC), Université de Paris",
  Where = "Paris, France",
  Activity = paste0(
    "Experiment creation and data collection for a study on memory, salience and bizarreness effect (reference: ",
    link("Pr Serge Nicolas", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Serge-Nicolas"),
    ")."
  )
)
)

if (short) {
  data <- data[1:1, ]
}

# Save for re-useability
write.csv(data, "data/experience_research.csv", row.names = FALSE, fileEncoding = "UTF-8")

detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```

## Teaching


```{r ExperienceTeaching}
data <- rbind(
  tibble(
  Position = "Invited Lecturer (Programming and Data Science)",
  Date = "2022",
  Institution = "University of Zurich",
  Where = "Zürich, Switzerland",
  Activity = paste0("Online workshop (24 h; PhD students): Advanced Python programming for signal processing and data analysis. Reference: ", link("Dr Maike Krannich", "https://www.psychologie.uzh.ch/de/studium/doktorat/team.html"), ".")
), tibble(
  Position = "Assistant Lecturer (Clinical Neuropsychology)",
  Date = "2017 - 18",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = paste0("Courses (192 h; bachelor \\& master students): Neurology and psychiatry (main neurodegenerative, neurological and psychiatric disorders), assessment (examination, diagnostic, psychometry), rehabilitation and psychotherapy (CBT, mindfulness-based therapies, cognitive rehabilitation, practice supervision), general neuroscience and psychology (neuroanatomy, emotion regulation...). Reference: ", link("Pr Isabelle Jambaqué", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Isabelle-Jambaque-Aubourg"), ".")
),tibble(
  Position = "Teaching Assistant (Differential Cognitive Psychology)",
  Date = "2015 - 17",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = "Courses (144 h; 1st \\& 2nd year students): Experimental methodology (assessment and related problems, scientific reasoning, psychometric properties of tests and questionnaires, statistics...) and introduction to concepts such as intelligence, personality and creativity. Reference: Dr Christophe Mouchiroud."
),tibble(
  Position = "Teaching Assistant (Cognitive Psychology)",
  Date = "2014 - 16",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = paste0("Courses (48 h; 3rd year students): Models of working memory, mental imagery and categorisation. Reference: ", link("Pr Todd Lubart", "https://lapea.recherche.parisdescartes.fr/membres-permanents/todd-lubart/"), ".")
),tibble(
  Position = "Teaching Assistant (University Services)",
  Date = "2013",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = "Courses (16 h; 1st year students): Introduction to the use of internet (internet security, anonymity, etc.) and on-line university services for first year students. Reference: Dr Christian Fondrat."
))


# Save for re-useability
write.csv(data, "data/experience_teaching.csv", row.names = FALSE, fileEncoding = "UTF-8")

detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```


## Clinical

```{r ExperienceClinical}
data <- rbind(tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2013 - 14",
  Institution = "Department of adult psychiatry, Pitié-Salpêtrière Hospital",
  Where = "Paris, France",
  Activity = paste0("Neuropsychology internship (512 h) under ", link("Dr Séverine Hatif", "https://fr.linkedin.com/in/hatif-severine-032596157"), ". Assessment and diagnostic of psychiatric or neurological illnesses among adults, as well as development and application of cognitive rehabilitation programs.")
),tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2012 - 13",
  Institution = "Department of geriatric psychiatry, Sainte-Anne Hospital",
  Where = "Paris, France",
  Activity = "Neuropsychology internship (304 h) under Emmanuel Guiliano. Assessment and diagnostic of psychiatric and neurological illnesses among an elderly population."
),tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2012",
  Institution = "Department of gerontology, La Porte Verte Hospital",
  Where = "Versailles, France",
  Activity = "Neuropsychology internship (96 h) under Sophie Fleury. Observation of assessment and diagnostic of memory related deficits such as neurodegenerative diseases, somatic ageing-related illnesses or depression."
))


# Save for re-useability
write.csv(data, "data/experience_clinical.csv", row.names = FALSE, fileEncoding = "UTF-8")

detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```


# Skills

## Language

\small

- **French**: Native
- **Polish**: Native
- **English**: Fluent
- **Italian**: B1 level (currently learning)

\normalsize

## Research

\small

My PhD, on the effect of reality beliefs on emotion, attempted at integrate my two core topics on interest: **reality bending** (manipulation and perception of reality) and **affective neuroscience** (the role of emotions, interoception, bodily signals in cognition). My first postdoc in Singapore led me to investigate a new layer of reality manipulation by working on a large project interested in the neurocognitive correlates of deception, funded by the Ministry of Defence. Over the years, I also had the opportunity of working on other topics, including **memory**, **cognitive control**, **mindfulness meditation** and **history of psychology**, providing me with a wide and multidisciplinary perspective and an international network of collaborations.

\normalsize

## Techniques and Methods

\small

I have developed strong technical expertise with several tools (EEG, bodily signals, Virtual Reality) and methods. In particular, I employ advanced statistical procedures (Bayesian framework, predictive and structural modelling, machine/deep learning) to address the scientific challenges that I encounter. In parallel, I develop open-source software, such as the `r link("\\textbf{easystats}", "https://github.com/easystats/easystats")` collection of R packages; `r link("\\textbf{NeuroKit}", "https://github.com/neuropsychology/NeuroKit")`, a Python package for neurophysiological signal processing; `r link("\\textbf{Pyllusion}", "https://github.com/realitybending/Pyllusion")`, a framework to generate visual illusions; or `r link("\\textbf{Neuropsydia}", "https://github.com/neuropsychology/Neuropsydia.py")`, a software to create experiments.

Initially created to increase the efficiency and quality of my own research, some of these tools have become quite popular and are actively used by the scientific community (e.g., the *easystats* packages have been downloaded more than 5 million times since their creation about 3 years ago, and *NeuroKit* has become one of the most popular toolbox for multimodal physiology).

## Open Science

My interest in improving accessibility, widening the usage of advanced methods and best practices by means of open access tools and tutorials, and staying active in open-software communities (e.g., on `r link("\\textbf{GitHub}", "https://github.com/DominiqueMakowski")` by answer technical and methodological questions, is motivated by the fact that, coming myself from a different background (clinical neuropsychology) in which programming, computer science and advanced statistics are not taught, I realized how harnessing such powerful tools can improve one's research (and quality of life) at many levels.

I fully endorse to the highest standards of open science, by sharing data and reproducible scripts of my experiments (see this `r link("\\textbf{Supplementary Materials Template}", "https://github.com/RealityBending/TemplateResults")` created to facilitate the sharing of additional material). Naturally, my concrete engagement in open, honest and reproducible science, is accompanied by the highest standards in terms of methodological rigour and ethical responsibility.



# Additional Training

<!-- \tiny -->
<!-- \emph{All the courses mentioned below were accredited or completion-certified.} -->
<!-- \normalsize -->


## Teaching

```{r TrainingTeaching}
data <- rbind(tibble(
  what = "CITI Certification",
  when = "2019",
  with = "Collaborative Institutional Training Initiative (ethics and scientific integrity in research)",
  where = "Online",
  details = NA
), tibble(
  what = "Academic Teaching Certificate",
  when = "2017",
  with = "Université of Paris (40h training in pedagogy and innovative teaching)",
  where = "France",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```


## Clinical

```{r TrainingClinical}
data <- rbind(tibble(
  what = "Certified Hypnotherapist",
  when = "2019",
  with = "National Guild of Hypnotists (100h - Note that although trained and qualified, I do not endorse hypnosis)",
  where = "Singapore",
  instructor = "Fauziah Shah",
  details = NA
), tibble(
  what = "Mindfulness based on Compassion and Insight (MBCI)",
  when = "2016",
  with = "Institute for psychiatry, Sainte-Anne Hospital (16h master class)",
  instructor = "Pr Pascal Delamillieure",
  where = "France",
  details = NA
), tibble(
  what = "First Aid Certificate",
  when = "2016",
  with = "Université de Paris (16h - level 1)",
  where = "France",
  instructor = NA,
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```

## Neuroimaging

```{r TrainingNeuroimaging}
data <- rbind(tibble(
  what = "Structural, Functional and Radiological Neuroanatomy",
  when = "2020",
  with = "Neurocourses UK (32h)",
  where = "Online",
  instructor = "Dr Paul Johns",
  details = NA
), tibble(
  what = "MRI Connectivity Analysis",
  when = "2015",
  with = "National Institute of Nuclear Sciences \\& Techniques - INSTN (32h)",
  where = "Marseille, France",
  instructor = "Dr Jorge L. Armony",
  details = NA
), tibble(
  what = "fMRI : Preprocessing and Analysis",
  when = "2014 - 15",
  with = "Sainte-Anne Hospital (32h)",
  where = "Paris, France",
  instructor = "Dr Sylvain Charron",
  details = NA
), tibble(
  what = "Signal Processing Theory and Application for EEG",
  when = "2014",
  with = "École Supérieure de Physique et de Chimie Industrielle - ESPCI (24h)",
  where = "Paris, France",
  instructor = "Dr François Vialatte",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```

## Statistics and Programming

```{r TrainingStatistics}
data <- rbind(tibble(
  what = "Creating Online Experiments in PsychoPy and Pavlovia",
  when = "2020",
  with = "University of Nottingham (24h)",
  where = "Online",
  instructor = "Dr Rebecca Hirst",
  details = NA
), tibble(
  what = "Scientific Programming with Python and Software Engineering Best Practices",
  when = "2016",
  with = "Telecom ParisTech (16h)",
  where = "Paris, France",
  instructor = "Dr Alexandre Gramfort",
  details = NA
), tibble(
  what = "P4N: Python for Neuroscience (and Psychology)",
  when = "2016",
  with = "University of Nottingham (24h)",
  where = "Nottingham, UK",
  instructor = "Dr Jon Peirce",
  details = NA
), tibble(
  what = "Machine Learning and Brain-to-Computer Interfaces",
  when = "2014",
  with = "École Supérieure de Physique et de Chimie Industrielle - ESPCI (16h)",
  where = "Paris, France",
  instructor = "Dr François Vialatte",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```


## Miscellaneous

```{r TrainingMisc}
data <- rbind(tibble(
  what = "History of Arts",
  when = "2017-- 18",
  with = "École du Louvre (74h)",
  where = "Paris, France",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```





# Research Track Record


## Scientific Impact


```{r ScientificImpactFigure, echo = FALSE, fig.height=3, fig.width=10, out.width="80%", fig.align="center"}
load("data/data_scholar.Rdata")
source("https://raw.githubusercontent.com/DominiqueMakowski/CV/main/functions.R")

plot_impact(data_scholar)
```


```{r ScientificImpact, echo = FALSE}
get_stats(data_scholar) |>
  knitr::kable(
    col.names = c(
      "\\textit{n}-Publications \\textit{(total)}",
      "\\textit{n}-1\\textsuperscript{st} author",
      "\\textit{n}-2\\textsuperscript{nd} author",
      "\\textit{n}-Senior author",
      "H-index",
      "Citations \\textit{(total)}"
    ),
    format = "latex",
    booktabs = TRUE,
    escape = FALSE
  ) %>%
  kableExtra::kable_styling(position = "center", font_size = 8, latex_options = "hold_position")
```



## Grants and Awards


```{r GrantsAwards}
data <- rbind(
  tibble(
  Name = paste0(link("TL@NTU's Behavioural and Communication Science Programme (BCSP) Grant", "https://www.ntu.edu.sg/temasek-labs/research-focus/programme", color = "333333"), " (co-PI)"),
  # Details = link("Cognitive, Neural and Social Factors involved in the Perception of Real vs. Fake Information", "https://fcl.ethz.ch/research/research-projects/NICE.html", color = "5D5D5D"),
  Details = "Cognitive, Neural and Social Factors involved in the Perception of Real vs. Fake Information",
  Date = "2022 - 25",
  Amount = "\\$915,427",
  Activity = NA
),tibble(
  Name = paste0(link("Singapore National Research Foundation's Intra-CREATE Grant", "https://researchgrant.gov.sg/Pages/GrantCallDetail.aspx?AXID=NRF2021-ITS008&CompanyCode=nrf", color = "333333"), " (co-PI)"),
  Details = link("A Neuroscientific investigation of the Interaction between Crowdedness and Environment typology (NICE)", "https://fcl.ethz.ch/research/research-projects/NICE.html", color = "5D5D5D"),
  Date = "2021 - 22",
  Amount = "\\$249,730",
  Activity = NA
),tibble(
  Name = paste0(link("NTU Presidential Postdoctoral Fellowship", "https://www.ntu.edu.sg/research/research-careers/presidential-postdoctoral-fellowship-(ppf)", color = "333333"), " (PI)"),
  Details = "'That's Fake News': Modulating the Neurocognitive Processes Underlying the Belief in Deceptive Information",
  Date = "2020 - 22",
  Amount = "\\$360,000",
  Activity = NA
),tibble(
  Name = link("Best Article Award (Psychonomic Society)", "https://www.psychonomic.org/page/2020BestArticleAwards", color = "333333") ,
  Details = paste0("Obtained for ", link("Makowski et al. (2019)", "https://dominiquemakowski.github.io/publication/makowski2019phenomenal/")),
  Date = "2020",
  Amount = "\\$1,000",
  Activity = NA
),tibble(
  Name = link("Commendation (Society for the Improvement of Psychological Science - SIPS)", "https://improvingpsych.org/mission/awards/", color = "333333") ,
  Details = paste0("Obtained for the bayestestR R package ", link("(Makowski et al., 2019)", "https://joss.theoj.org/papers/10.21105/joss.01541")),
  Date = "2020",
  Amount = "N/A",
  Activity = NA
),tibble(
  Name = link("Ministerial PhD scholarship", "https://improvingpsych.org/mission/awards/", color = "333333") ,
  Details = "Three years of PhD fully funded by the French Ministry of Research",
  Date = "2014 - 17",
  Amount = "€80,000",
  Activity = NA
))

detailed_entries(data, Details, Date, Name, Amount, Activity, .protect = FALSE)
```


## Editorial Responsibilities


```{r EditorialResponsabilities}
data <- rbind(tibble(
  Position = "Associate Editor",
  Where = link("Frontiers in Psychology: \\textit{Quantitative Psychology and Measurement}", "https://www.frontiersin.org/journals/all/sections/quantitative-psychology-and-measurement", color = "333333"),
  Date = "2020 - present",
  Location = NA,
  Activity = NA
),tibble(
  Position = "Regular Reviewer",
  Where = link("Journal of Open Source Software", "https://joss.theoj.org/", color = "333333"),
  Date = "2018 - present",
  Location = NA,
  Activity = NA
),tibble(
  Position = "Reviewer",
  Where = "Biological Psychiatry, Personality and Individual Differences, Scientific Reports, Acta Psychologica, ...",
  Date = "2017 - present",
  Location = NA,
  Activity = NA
))

# brief_entries(data, Where, Date, Position, .protect = FALSE)
detailed_entries(data, Where, Date, Position, Location, Activity, .protect = FALSE)
```

## Academic Responsibilities

```{r AcademicResponsabilities}
data <- rbind(tibble(
  Position = "Elected Representative",
  Details = "Representation of the PhD students at the university level",
  Where = "ED261-3CH doctoral school",
  Date = "2016 - 18",
  Activity = NA
),tibble(
  Position = "Community Manager",
  Details = "Organization of seminars, local conferences and social events",
  Where = "Memory \\& Cognition Lab",
  Date = "2014 - 15",
  Activity = NA
),tibble(
  Position = "Active Member",
  Details = "Organization of social events for students",
  Where = "Student Association (BDE)",
  Date = "2009 - 12",
  Activity = NA
))

detailed_entries(data, Details, Date, Position, Where, Activity, .protect = FALSE)
```

<!-- ## Collaborations -->

# Teaching Record


## Academic

\small


I have given academic lectures (total hours since 2014: **400**) on the following topics:

- **Neuropsychology** (*192 hours; 2nd year, 3rd year and master level*)
    - Clinical Neuropsychology \scriptsize(Neuropsychological syndromes; Neuropsychological examination and diagnostic; Cognitive rehabilitation; Clinical practice supervision; Neuropsychology in psychiatry)\normalsize
    - Cognitive Neuroscience \scriptsize(Neuroanatomy; Emotion Regulation; Mindfulness; Memory; Neuroimaging)\normalsize
- **Differential Psychology** (*144 hours; 1st year level*)
    - Hands-on Lectures \scriptsize(Experimental Methodology; Scientific Reasoning; Psychometric properties of tests and questionnaires; Introductory Statistics)\normalsize
    - Theory \scriptsize(Intelligence; Personality; Creativity)\normalsize
- **Cognitive Psychology** (*48 hours; 3rd year level*):
    - Working memory
    - Mental imagery and categorisation
<!-- - **Programming and Data Science** (*24 hours*):  -->
<!--     - Python Programming -->
<!--     - Signal Processing -->
<!--     - Statistics -->
- **Other** (*16 hours*): Internet; Research Ethics; Digital Rights

\normalsize

## Technical

\small

I have performed several technical courses (typically in-lab training) on topics like:

- Statistics using R
- Experiment creation using Python
- How to acquire electrophysiological (EDA, ECG, EMG) signal using *BIOPAC* and *AcqKnowledge®*
- How to ask and handle sensitive personal information about patients or participants

\normalsize

<!-- ## Mentoring -->

<!-- I have mentored more than 5 full-time research assistants.  -->

<!-- I have also co-supervised bachelor and master students for their research projects.  -->



# Publications

```{r, child=c('publications.Rmd')}
```


# References

\small

Do not hesitate to contact them of any inquiry.

- **Pr Annabel Chen** (Postdoc supervisor): AnnabelChen@ntu.edu.sg
- **Dr Marco Sperduti** (PhD mentor): marco.sperduti@parisdescartes.fr
- **Pr Pascale Piolino** (PhD cosupervisor): pascale.piolino@parisdescartes.fr
- **Pr Serge Nicolas** (PhD cosupervisor): serge.nicolas@parisdescartes.fr

\normalsize
