---
name: Dominique
surname: Makowski
profilepic: "./img/profile.png"
position: "Research Fellow"
qualifications: "PhD"
address: "Nanyang Technological University, Singapore"
# phone: +1 22 3333 4444
www: dominiquemakowski.github.io
email: "dom.makowski@gmail.com"
twitter: Dom_Makowski
github: DominiqueMakowski
# linkedin: dominiquemakowski
# orcid: "0000-0001-5375-9967"
aboutme: |
  \RaggedRight Trained as neuropsychologist, I am currently a postdoc in Singapore researching aspects of reality bending (e.g., neuroscience of deception, perception of fake news, altered states of consciousness), the role of the body and emotions in cognition (e.g., emotion regulation and interoception), and methodology (statistics, programming, and neurophysiological techniques).
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "1976D2"
output: 
  vitae::awesomecv:
    page_total: true
    keep_md: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(ggplot2)

link <- function(txt, url, color = "1976D2") {
  paste0("\\href{", url, "}{\\color[HTML]{", color, "}{", txt, "}}")
}

short <- FALSE
```

# Current Position

```{r CurrentEmployment}
data <- tibble(
  what = "Presidential Postdoctoral Fellow",
  when = "2020 - Present",
  with = "Clinical Brain Lab, Nanyang Technological University (NTU)",
  where = "Singapore",
  details = c(
    paste(
      "The",
      link("NTU Presidential Postdoc award", "https://www.ntu.edu.sg/research/research-careers/presidential-postdoctoral-fellowship-(ppf)"),
      "funded two years of postdoc to develop my own research direction"
    ),
    paste(
      "The team I lead (see ",
       link("Reality Bending", "https://realitybending.github.io/"),
      ") works on the neurocognitive and affective processes underlying the beliefs in fake vs. real stimuli (fake news, fiction, ...)"
    ),
    paste(
      "Reference:",
      link("Pr Annabel Chen", "https://www.clinicalbrain.org/author/annabel-chen/")
    )
  )
)

detailed_entries(data, with, when, what, where, details, .protect = FALSE)
```



# Education

```{r Education}
data <- rbind(tibble(
  what = "Doctor of Philosophy (PhD) - Psychology",
  when = "2014 - 18",
  with = "Université de Paris",
  where = "France",
  details = paste0(
    "Thesis: Cognitive Neuropsychology of Implicit Emotion Regulation through Fictional Reappraisal (supervised by ",
    link("Pr Serge Nicolas", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Serge-Nicolas"),
    " \\& ",
    link("Pr Pascale Piolino", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Pascale-Piolino"),
    ")"
  )
), tibble(
  what = "Certified Psychotherapist - Cognitive Behavioural Therapy (CBT)",
  when = "2014 - 17",
  with = "French Association for Cognitive Behavioural Therapy (AFTCC)",
  where = "France",
  details = c(
    "Thesis: Cognitive Behavioural Therapy for two Patients: One suffering from Motivation Disorder associated with Dysthymia and the other from Social Anxiety (supervised by Sophie Kindynis)"
  )
), tibble(
  what = "Master of Science (MSc) - Neuropsychology and Cognitive Psychology",
  when = "2012 - 14",
  with = "Université de Paris",
  where = "France",
  details = c(
    paste0("Second year thesis: How the Study of Emotions in Schizophrenia enlight the Paradox of Fiction (supervised by ", link("Pr Pascale Piolino", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Pascale-Piolino"), ")"),
    paste0("First year thesis: The Cognitive Development of the Aesthetic Judgement in Children and Adults (supervised by ", link("Pr Sandrine Rossi", "https://www.researchgate.net/profile/Sandrine-Rossi"), ")")
  )
), tibble(
  what = "Bachelor of Arts (BA) - Psychology",
  when = "2009 - 12",
  with = "Université de Paris",
  where = "France",
  details = NA
))

if (short) {
  data <- data[1:3, ]
  data$details <- NA
}

detailed_entries(data, with, when, what, where, details, .protect = FALSE)
```

# Additional Training

<!-- \tiny -->
<!-- \emph{All the courses mentioned below were accredited or completion-certified.} -->
<!-- \normalsize -->


## Teaching

```{r TrainingTeaching}
data <- rbind(tibble(
  what = "CITI Certification",
  when = "2019",
  with = "Collaborative Institutional Training Initiative (ethics and scientific integrity in research)",
  where = "Online",
  details = NA
), tibble(
  what = "Academic Teaching Certificate",
  when = "2017",
  with = "Université of Paris (40h training in pedagogy and innovative teaching)",
  where = "France",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```


## Clinical

```{r TrainingClinical}
data <- rbind(tibble(
  what = "Certified Hypnotherapist",
  when = "2019",
  with = "National Guild of Hypnotists (100h - Note that although trained and qualified, I do not endorse hypnosis)",
  where = "Singapore",
  instructor = "Fauziah Shah",
  details = NA
), tibble(
  what = "Mindfulness based on Compassion and Insight (MBCI)",
  when = "2016",
  with = "Institute for psychiatry, Sainte-Anne Hospital (16h master class)",
  instructor = "Pr Pascal Delamillieure",
  where = "France",
  details = NA
), tibble(
  what = "First Aid Certificate",
  when = "2016",
  with = "Université de Paris (16h - level 1)",
  where = "France",
  instructor = NA,
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```

## Neuroimaging

```{r TrainingNeuroimaging}
data <- rbind(tibble(
  what = "Structural, Functional and Radiological Neuroanatomy",
  when = "2020",
  with = "Neurocourses UK (32h)",
  where = "Online",
  instructor = "Dr Paul Johns",
  details = NA
), tibble(
  what = "MRI Connectivity Analysis",
  when = "2015",
  with = "National Institute of Nuclear Sciences \\& Techniques - INSTN (32h)",
  where = "Marseille, France",
  instructor = "Dr Jorge L. Armony",
  details = NA
), tibble(
  what = "fMRI : Preprocessing and Analysis",
  when = "2014 - 15",
  with = "Sainte-Anne Hospital (32h)",
  where = "Paris, France",
  instructor = "Dr Sylvain Charron",
  details = NA
), tibble(
  what = "Signal Processing Theory and Application for EEG",
  when = "2014",
  with = "École Supérieure de Physique et de Chimie Industrielle - ESPCI (24h)",
  where = "Paris, France",
  instructor = "Dr François Vialatte",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```

## Statistics and Programming

```{r TrainingStatistics}
data <- rbind(tibble(
  what = "Creating Online Experiments in PsychoPy and Pavlovia",
  when = "2020",
  with = "University of Nottingham (24h)",
  where = "Online",
  instructor = "Dr Rebecca Hirst",
  details = NA
), tibble(
  what = "Scientific Programming with Python and Software Engineering Best Practices",
  when = "2016",
  with = "Telecom ParisTech (16h)",
  where = "Paris, France",
  instructor = "Dr Alexandre Gramfort",
  details = NA
), tibble(
  what = "P4N: Python for Neuroscience (and Psychology)",
  when = "2016",
  with = "University of Nottingham (24h)",
  where = "Nottingham, UK",
  instructor = "Dr Jon Peirce",
  details = NA
), tibble(
  what = "Machine Learning and Brain-to-Computer Interfaces",
  when = "2014",
  with = "École Supérieure de Physique et de Chimie Industrielle - ESPCI (16h)",
  where = "Paris, France",
  instructor = "Dr François Vialatte",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```


## Miscellaneous

```{r TrainingMisc}
data <- rbind(tibble(
  what = "History of Arts",
  when = "2017-- 18",
  with = "École du Louvre (74h)",
  where = "Paris, France",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```




# Skills

## Language

\small

- **French**: Native
- **Polish**: Native
- **English**: Fluent
- **Italian**: B1 level (currently learning)

\normalsize

## Research

\small

My PhD, on the effect of reality beliefs on emotion, attempted at integrate my two core topics on interest: **reality bending** (manipulation and perception of reality) and **affective neuroscience** (the role of emotions, interoception, bodily signals in cognition). My first postdoc in Singapore led me to investigate a new layer of reality manipulation by working on a large project interested in the neurocognitive correlates of deception, funded by the Ministry of Defence. Over the years, I also had the opportunity of working on other topics, including **memory**, **cognitive control**, **mindfulness meditation** and **history of psychology**, providing me with a wide and multidisciplinary perspective and an international network of collaborations.

\normalsize

## Techniques and Methods

\small

I have developed strong technical expertise with several tools (EEG, bodily signals, Virtual Reality) and methods. In particular, I employ advanced statistical procedures (Bayesian framework, predictive and structural modelling, machine/deep learning) to address the scientific challenges that I encounter. In parallel, I develop open-source software, such as the `r link("\\textbf{easystats}", "https://github.com/easystats/easystats")` collection of R packages; `r link("\\textbf{NeuroKit}", "https://github.com/neuropsychology/NeuroKit")`, a Python package for neurophysiological signal processing; `r link("\\textbf{Pyllusion}", "https://github.com/realitybending/Pyllusion")`, a framework to generate visual illusions; or `r link("\\textbf{Neuropsydia}", "https://github.com/neuropsychology/Neuropsydia.py")`, a software to create experiments. 

Initially created to increase the efficiency and quality of my own research, some of these tools have become quite popular and are actively used by the scientific community (e.g., the *easystats* packages have been downloaded more than 5 million times since their creation about 3 years ago, and *NeuroKit* has become one of the most popular toolbox for multimodal physiology). 

## Open Science

My interest in improving accessibility, widening the usage of advanced methods and best practices by means of open access tools and tutorials, and staying active in open-software communities (e.g., on `r link("\\textbf{GitHub}", "https://github.com/DominiqueMakowski")` by answer technical and methodological questions, is motivated by the fact that, coming myself from a different background (clinical neuropsychology) in which programming, computer science and advanced statistics are not taught, I realized how harnessing such powerful tools can improve one's research (and quality of life) at many levels. 

I fully endorse to the highest standards of open science, by sharing data and reproducible scripts of my experiments (see this `r link("\\textbf{Supplementary Materials Template}", "https://github.com/RealityBending/TemplateResults")` that I created to facilitate the sharing of additional material). Naturally, my concrete engagement in open, honest and reproducible science, is accompanied by the highest standards in terms of methodological rigour and ethical responsibility.



# Research Track Record


## Scientific Impact


```{r ScientificImpactFigure, echo = FALSE, fig.height=3, fig.width=10, out.width="80%", fig.align="center"}
load("data/data_scholar.Rdata")
source("https://raw.githubusercontent.com/DominiqueMakowski/CV/main/functions.R")

plot_impact(data_scholar)
```


```{r ScientificImpact, echo = FALSE}
get_stats(data_scholar) |>
  knitr::kable(
    col.names = c(
      "\\textit{n}-Publications \\textit{(total)}",
      "\\textit{n}-1\\textsuperscript{st} author",
      "\\textit{n}-2\\textsuperscript{nd} author",
      "\\textit{n}-Senior author",
      "H-index",
      "Citations \\textit{(total)}"
    ),
    format = "latex",
    booktabs = TRUE,
    escape = FALSE
  ) %>%
  kableExtra::kable_styling(position = "center", font_size = 8, latex_options = "hold_position")
```



## Grants and Awards


```{r GrantsAwards}
data <- rbind(tibble(
  Name = paste0("co-PI: ", link("Singapore National Research Foundation's Intra-CREATE Grant", "https://researchgrant.gov.sg/Pages/GrantCallDetail.aspx?AXID=NRF2021-ITS008&CompanyCode=nrf", color = "333333")),
  Details = link("A Neuroscientific investigation of the Interaction between Crowdedness and Environment typology (NICE)", "https://fcl.ethz.ch/research/research-projects/NICE.html", color = "5D5D5D"),
  Date = "2021 - 22",
  Amount = "\\$249,730",
  Activity = NA
),tibble(
  Name = paste0("PI: ", link("NTU Presidential Postdoctoral Fellowship", "https://www.ntu.edu.sg/research/research-careers/presidential-postdoctoral-fellowship-(ppf)", color = "333333")),
  Details = "'That's Fake News': Modulating the Neurocognitive Processes Underlying the Belief in Deceptive Information",
  Date = "2020 - 22",
  Amount = "\\$360,000",
  Activity = NA
),tibble(
  Name = link("Best Article Award (Psychonomic Society)", "https://www.psychonomic.org/page/2020BestArticleAwards", color = "333333") ,
  Details = paste0("Obtained for ", link("Makowski et al. (2019)", "https://dominiquemakowski.github.io/publication/makowski2019phenomenal/")),
  Date = "2020",
  Amount = "\\$1,000",
  Activity = NA
),tibble(
  Name = link("Commendation (Society for the Improvement of Psychological Science - SIPS)", "https://improvingpsych.org/mission/awards/", color = "333333") ,
  Details = paste0("Obtained for the bayestestR R package ", link("(Makowski et al., 2019)", "https://joss.theoj.org/papers/10.21105/joss.01541")),
  Date = "2020",
  Amount = "N/A",
  Activity = NA
),tibble(
  Name = link("Ministerial PhD scholarship", "https://improvingpsych.org/mission/awards/", color = "333333") ,
  Details = "Three years of PhD fully funded by the French Ministry of Research",
  Date = "2014 - 17",
  Amount = "€80,000",
  Activity = NA
))

detailed_entries(data, Details, Date, Name, Amount, Activity, .protect = FALSE)
```


## Editorial Responsibilities


```{r EditorialResponsabilities}
data <- rbind(tibble(
  Position = "Associate Editor",
  Where = link("Frontiers in Psychology: \\textit{Quantitative Psychology and Measurement}", "https://www.frontiersin.org/journals/all/sections/quantitative-psychology-and-measurement", color = "333333"),
  Date = "2020 - present",
  Location = NA,
  Activity = NA
),tibble(
  Position = "Regular Reviewer",
  Where = link("Journal of Open Source Software", "https://joss.theoj.org/", color = "333333"),
  Date = "2018 - present",
  Location = NA,
  Activity = NA
),tibble(
  Position = "Reviewer",
  Where = "Biological Psychiatry, Personality and Individual Differences, Scientific Reports, Acta Psychologica, ...",
  Date = "2017 - present",
  Location = NA,
  Activity = NA
))

# brief_entries(data, Where, Date, Position, .protect = FALSE)
detailed_entries(data, Where, Date, Position, Location, Activity, .protect = FALSE)
```

## Academic Responsibilities

```{r AcademicResponsabilities}
data <- rbind(tibble(
  Position = "Elected Representative",
  Details = "Representation of the PhD students at the university level",
  Where = "ED261-3CH doctoral school",
  Date = "2016 - 18",
  Activity = NA
),tibble(
  Position = "Community Manager",
  Details = "Organization of seminars, local conferences and social events",
  Where = "Memory \\& Cognition Lab",
  Date = "2014 - 15",
  Activity = NA
),tibble(
  Position = "Active Member",
  Details = "Organization of social events for students",
  Where = "Student Association (BDE)",
  Date = "2009 - 12",
  Activity = NA
))

detailed_entries(data, Details, Date, Position, Where, Activity, .protect = FALSE)
```

<!-- ## Collaborations -->

# Teaching Record


## Academic

\small


I have given academic lectures (total hours since 2014: **400**) on the following topics:

- **Neuropsychology** (*192 hours; 2nd year, 3rd year and master level*)
    - Clinical Neuropsychology \scriptsize(Neuropsychological syndromes; Neuropsychological examination and diagnostic; Cognitive rehabilitation; Clinical practice supervision; Neuropsychology in psychiatry)\normalsize
    - Cognitive Neuroscience \scriptsize(Neuroanatomy; Emotion Regulation; Mindfulness; Memory; Neuroimaging)\normalsize
- **Differential Psychology** (*144 hours; 1st year level*)
    - Hands-on Lectures \scriptsize(Experimental Methodology; Scientific Reasoning; Psychometric properties of tests and questionnaires; Introductory Statistics)\normalsize
    - Theory \scriptsize(Intelligence; Personality; Creativity)\normalsize
- **Cognitive Psychology** (*48 hours; 3rd year level*):
    - Working memory
    - Mental imagery and categorisation
- **Other** (*16 hours*): Internet; Research Ethics; Digital Rights

\normalsize

## Technical

\small

I have performed several technical courses (typically in-lab training) on topics like:

- Statistics using R
- Experiment creation using Python
- How to acquire electrophysiological (EDA, ECG, EMG) signal using *BIOPAC* and *AcqKnowledge®*
- How to ask and handle sensitive personal information about patients or participants

\normalsize

# Experience

## Research

```{r ExperienceResearch}
data <- rbind(tibble(
  Position = "Research Fellow",
  Date = "2019 - 20",
  Institution = "Clinical Brain Lab, Nanyang Technological University (NTU)",
  Where = "Singapore",
  Activity = paste0(
    "First postdoc position, working on a project funded by the ministry of defence about the neurocognitive correlates of deception. Responsible for studies design and completion, data analysis, publications and co-supervision of one PhD student, two research assistants and several graduate and undergraduate students (reference: ",
    link("Pr Annabel Chen", "https://www.clinicalbrain.org/author/annabel-chen/"),
    ")."
  )
), tibble(
  Position = "Research Assistant",
  Date = "2012",
  Institution = "Developmental Psychology Lab (LaPsyDé), Université de Paris",
  Where = "Paris, France",
  Activity = paste0(
    "Data collection for a study ",
    link("(Borst, 2016)", "http://psycnet.apa.org/journals/emo/13/5/811/"),
    " on emotions and mental rotation (reference: ", link("Pr Grégoire Borst", "https://www.lapsyde.com/gregoire-borst"),
    ")."
  )
), tibble(
  Position = "Research Assistant",
  Date = "2011",
  Institution = "Memory \\& Cognition Lab (LMC), Université de Paris",
  Where = "Paris, France",
  Activity = paste0(
    "Experiment creation and data collection for a study on memory, salience and bizarreness effect (reference: ",
    link("Pr Serge Nicolas", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Serge-Nicolas"),
    ")."
  )
))

if (short) {
  data <- data[1:1, ]
}

# Save for re-useability
write.csv(data, "data/experience_research.csv", row.names = FALSE, fileEncoding = "UTF-8")

detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```


## Clinical

```{r ExperienceClinical}
data <- rbind(tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2013 - 14",
  Institution = "Department of adult psychiatry, Pitié-Salpêtrière Hospital",
  Where = "Paris, France",
  Activity = paste0("Neuropsychology internship (512 h) under ", link("Dr Séverine Hatif", "https://fr.linkedin.com/in/hatif-severine-032596157"), ". Assessment and diagnostic of psychiatric or neurological illnesses among adults, as well as development and application of cognitive rehabilitation programs.")
),tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2012 - 13",
  Institution = "Department of geriatric psychiatry, Sainte-Anne Hospital",
  Where = "Paris, France",
  Activity = "Neuropsychology internship (304 h) under Emmanuel Guiliano. Assessment and diagnostic of psychiatric and neurological illnesses among an elderly population."
),tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2012",
  Institution = "Department of gerontology, La Porte Verte Hospital",
  Where = "Versailles, France",
  Activity = "Neuropsychology internship (96 h) under Sophie Fleury. Observation of assessment and diagnostic of memory related deficits such as neurodegenerative diseases, somatic ageing-related illnesses or depression."
))


# Save for re-useability
write.csv(data, "data/experience_clinical.csv", row.names = FALSE, fileEncoding = "UTF-8")

detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```

## Teaching


```{r ExperienceTeaching}
data <- rbind(tibble(
  Position = "Lecturer (Clinical Neuropsychology)",
  Date = "2017 - 18",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = paste0("Courses (192 h; bachelor \\& master students): Neurology and psychiatry (main neurodegenerative, neurological and psychiatric disorders), assessment (examination, diagnostic, psychometry), rehabilitation and psychotherapy (CBT, mindfulness-based therapies, cognitive rehabilitation, practice supervision), general neuroscience and psychology (neuroanatomy, emotion regulation...). Reference: ", link("Pr Isabelle Jambaqué", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Isabelle-Jambaque-Aubourg"), ".")
),tibble(
  Position = "Teaching Assistant (Differential Cognitive Psychology)",
  Date = "2015 - 17",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = "Courses (144 h; 1st \\& 2nd year students): Experimental methodology (assessment and related problems, scientific reasoning, psychometric properties of tests and questionnaires, statistics...) and introduction to concepts such as intelligence, personality and creativity. Reference: Dr Christophe Mouchiroud."
),tibble(
  Position = "Teaching Assistant (Cognitive Psychology)",
  Date = "2014 - 16",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = paste0("Courses (48 h; 3rd year students): Models of working memory, mental imagery and categorisation. Reference: ", link("Pr Todd Lubart", "https://lapea.recherche.parisdescartes.fr/membres-permanents/todd-lubart/"), ".")
),tibble(
  Position = "Teaching Assistant (University Services)",
  Date = "2013",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = "Courses (16 h; 1st year students): Introduction to the use of internet (internet security, anonymity, etc.) and on-line university services for first year students. Reference: Dr Christian Fondrat."
))


# Save for re-useability
write.csv(data, "data/experience_teaching.csv", row.names = FALSE, fileEncoding = "UTF-8")

detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```

# Publications

## Reality Perception and Manipulation

\scriptsize

**Makowski, D.**, Lau, Z. J., Pham, T., Ayache, J., Sperduti, M., Sumich, A., Heym, N. & Chen, S., A. (*under review*). Psychological Determinants of the Susceptibility to COVID-19 Fake News.

**Makowski, D.**, Lau, Z. J., Pham, T., Boyce, W. P. \& Chen, S. A. (2021). [A Parametric Framework to Generate Visual Illusions using Python](https://dominiquemakowski.github.io/publication/makowski2021parametric/makowski2021parametric.pdf). *Perception*, 50(11), 950-965.

**Makowski, D.**, Pham, T., Lau, Z. J., Raine, A., & Chen, S. H. (2021). [The Structure of Deception: Validation of the Lying Profile Questionnaire](https://dominiquemakowski.github.io/publication/makowski2021structure/makowski2021structure.pdf). *Current Psychology*, 1-16.

**Makowski, D.**, Sperduti, M., Pelletier, J., Blondé, P., La Corte, V., Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S., & Piolino, P. (2019). [Phenomenal, Bodily and Brain Correlates of Fictional Reappraisal as an Implicit Emotion Regulation Strategy](https://dominiquemakowski.github.io/publication/makowski2019phenomenal/makowski2019phenomenal.pdf). *Cognitive, Affective, & Behavioral Neuroscience*, 19(4), 1-21.

**Makowski, D.**\*, Sperduti, M.\*, Nicolas, S. & Piolino, P. (2017). ["*Being there*" and remembering it: Presence improves Memory Encoding](https://dominiquemakowski.github.io/publication/makowski2017being/makowski2017being.pdf). *Consciousness & Cognition, 53*, 194–202.

Sperduti, M.\*, **Makowski, D.**\*, Arcangeli, M., Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J. & Piolino, P. (2017). [The Distinctive Role of Executive Functions in Implicit Emotion Regulation](https://dominiquemakowski.github.io/publication/sperduti2017distinctive/sperduti2017distinctive.pdf). *Acta Psychologica, 173*, 13-20.

Tuena, C., Serino, S., Gaston-Bellegarde, A., Orriols, E., **Makowski, D.**, Riva, G. & Piolino, P. (2017). [How Virtual Embodiment Affects Episodic Memory Functioning: a Proof-of-Concept Study](https://dominiquemakowski.github.io/publication/tuena2017virtual/tuena2017virtual.pdf), *Annual Review of Cybertherapy and Telemedicine*, 15, 93-107.

Sperduti, M.\*, Arcangeli, M.\*, **Makowski, D.**, Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J. \& Piolino, P. (2016). [The paradox of fiction: Emotional response toward fiction and the modulatory role of self-relevance](https://dominiquemakowski.github.io/publication/sperduti2016paradox/sperduti2016paradox.pdf). *Acta psychologica*, 165, 53-59.


\normalsize

## Neurophysiology, Emotion Regulation and Interoceptive Processes

\scriptsize

Lau, Z. J.\*, Pham, T.\*, Chen, S. A., & **Makowski, D.** (*under review*). Brain Entropy, Fractal Dimensions and Predictability: A Review of Complexity Measures for EEG in Healthy and Neuropsychiatric Populations. *PsyArXiv*.

Pham, T., Lau, Z. J., Chen, S. H. A., & **Makowski, D.** (2021). [Heart Rate Variability in Psychology: A Review of HRV Indices and an Analysis Tutorial](https://www.mdpi.com/1424-8220/21/12/3998). *Sensors, 21*(12), 3998.

**Makowski, D.**, Pham, T., Lau, Z. J., Brammer, J. C., Lespinasse, F., Pham, H., Schötzel, C., & Chen, S. A. (2021). [NeuroKit2: A Python Toolbox for Neurophysiological Signal Processing](https://dominiquemakowski.github.io/publication/makowski2021neurokit/makowski2021neurokit.pdf). *Behavior Research Methods*, 1-8.

**Makowski, D.**, Sperduti, M., Blondé, P., Nicolas, S., & Piolino, P. (2019). [The heart of cognitive control: Cardiac phase modulates processing speed and inhibition](https://dominiquemakowski.github.io/publication/makowski2019heart/makowski2019heart.pdf). *Psychophysiology, 57*(3).

**Makowski, D.**, Sperduti, M., Lavallée, S., Nicolas, S., & Piolino, P. (2019). [Adaptation and Validation of a Short French Version of the Affective Style Questionnaire](https://dominiquemakowski.github.io/publication/makowski2019adaptation/makowski2019adaptation.pdf). *International Journal of Cognitive Therapy, 13*(2), 146–158.

**Makowski, D.**\*, Sperduti, M.\*, Lavallée, S., Nicolas, S. & Piolino, P. (2019). [Dispositional mindfulness attenuates the emotional attentional blink](https://dominiquemakowski.github.io/publication/makowski2019dispositional/makowski2019dispositional.pdf). *Consciousness & Cognition, 67*, 16–25.

**Makowski, D.**, Sperduti, M., Blanchet, S., Nicolas, S. & Piolino, P. (2015). [Régulation Emotionnelle face au Déclin Cognitif dans le Vieillissement : Un Faux Paradoxe ? | Emotion regulation and the cognitive decline in aging: beyond the paradox](https://dominiquemakowski.github.io/publication/makowski2015emotion/makowski2015emotion.pdf). *Gériatrie et Psychologie Neuropsychiatrie du Vieillissement*, 13(3), 301-8.

\normalsize



## Statistics

\scriptsize

Lüdecke, D., Patil, I., Ben-Shachar, M., Wiernik, B., Waggoner, P., & **Makowski, D.** (2021). [see: An R Package for Visualizing Statistical Models](https://joss.theoj.org/papers/10.21105/joss.03393). *Journal of Open Source Software, 6*(64), 3393.

Lüdecke, D., Ben-Shachar, M., Patil, I., Waggoner, P., & **Makowski, D.** (2021). [performance: An R Package for Assessment, Comparison and Testing of Statistical Models](https://joss.theoj.org/papers/10.21105/joss.03139). *Journal of Open Source Software, 6*(60), 3139.

Ben-Shachar, M. S., Lüdecke, D., & **Makowski, D.** (2020). [effectsize: Estimation of Effect Size Indices and Standardized Parameters](https://joss.theoj.org/papers/10.21105/joss.02815). *Journal of Open Source Software, 5*(56), 2815.

Lüdecke, D., Ben-Shachar, M. S., Patil, I., & **Makowski, D.** (2020). [parameters: Extracting, Computing and Exploring the Parameters of Statistical Models using R](https://joss.theoj.org/papers/10.21105/joss.02445). *Journal of Open Source Software, 5*(53), 2445.

**Makowski, D.**, Ben-Shachar, M. S., Patil, I., & Lüdecke, D. (2020). [Methods and Algorithms for Correlation Analysis in R](https://joss.theoj.org/papers/10.21105/joss.02306). *Journal of Open Source Software, 5*(51), 2306.

**Makowski, D.**, Ben-Shachar, M. S., Chen, S. H., & Lüdecke, D. (2019). [Indices of Effect Existence and Significance in the Bayesian Framework](https://dominiquemakowski.github.io/publication/makowski2019indices/makowski2019indices.pdf). *Frontiers in Psychology, 10*.

**Makowski, D.**, Ben-Shachar, M., & Lüdecke, D. (2019). [bayestestR: Describing effects and their uncertainty, existence and significance within the Bayesian framework](https://joss.theoj.org/papers/10.21105/joss.01541). *Journal of Open Source Software, 4*(40), 1541.

Lüdecke, D., Waggoner, P., & **Makowski, D.** (2019). [insight: A unified interface to access information from model objects in R](https://joss.theoj.org/papers/10.21105/joss.01412). *Journal of Open Source Software*, 4(38), 1412.

**Makowski, D** (2018). [The psycho Package: An Efficient and Publishing-Oriented Workflow for Psychological Science](https://dominiquemakowski.github.io/publication/makowski2018psycho/makowski2018psycho.pdf). *Journal of Open Source Software, 3*(22), 470.

\normalsize

## Miscellaneous

\scriptsize

Lee, H., Jacquot, A., **Makowski, D.**, Arcangeli, M., Dokic, J., Piolino, P., & Sperduti, M. (*under review*). [Beauty is in the eye of the beholder: Evidence from a common mnemonic advantage between aesthetics judgement and self-reference](https://dominiquemakowski.github.io/publication/lee2021beauty/lee2021beauty.pdf). *PsyArXiv*.

<!-- TODO: fix page number -->
Blondé, P., Sperduti, M., **Makowski, D.**, & Piolino, P. (2021). [Bored, distracted, and forgetful: The impact of mind wandering and boredom on memory encoding](https://journals.sagepub.com/doi/abs/10.1177/17470218211026301). *Quarterly Journal of Experimental Psychology*, 174702182110263. 

Blondé, P., **Makowski D.**, Sperduti, M., & Piolino, P. (2020). [In Medio Stat Virtus: intermediate levels of mind wandering improve episodic memory encoding in a virtual environment](https://dominiquemakowski.github.io/publication/blonde2020medio/blonde2020medio.pdf). *Psychological Research, 85*(4), 1613–1625.

<!-- TODO: fix page number -->
Girardeau, J. C., Blondé, P., **Makowski D.**, Abram, M., Piolino, P., & Sperduti, M. (2020). [The impact of state and dispositional mindfulness on prospective memory: A virtual reality study](https://dominiquemakowski.github.io/publication/girardeau2020impact/girardeau2020impact.pdf). *Consciousness and Cognition, 81*, 102920.

**Makowski, D.**, Dutriaux, L. (2017). [Neuropsydia.py: A Python Module for Creating Experiments, Tasks and Questionnaires](https://joss.theoj.org/papers/10.21105/joss.00259), *Journal of Open Source Software, 2*(19), 259.

Sperduti, M., Armougum, A., **Makowski, D.**, & Piolino, P. (2017). [Interaction between attentional systems and episodic memory encoding: the impact of conflict on binding of information](https://dominiquemakowski.github.io/publication/sperduti2017interaction/sperduti2017interaction.pdf), *Experimental Brain Research*, 235(12), 3553-3560.

Nicolas, S., & **Makowski, D**. (2017). [Centenaire Ribot (I). La réception de l'oeuvre de Théodule Ribot chez l'éditeur Ladrange (1870-1873)](https://dominiquemakowski.github.io/publication/nicolas2017centenaire/nicolas2017centenaire.pdf). *Bulletin de Psychologie*, 70(3), 163-178.

Sperduti, M., **Makowski, D.**, Blondé, P. & Piolino, P. (2017). [Meditation and successful aging: can meditative practices counteract age-related cognitive decline?](https://dominiquemakowski.github.io/publication/sperduti2017meditation/sperduti2017meditation.pdf), *Gériatrie et Psychologie Neuropsychiatrie du Vieillissement*, 15(2), 205-13.

Nicolas, S., & **Makowski, D**. (2016). [Can mental fatigue be measured by Weber's compass? Alfred Binet's answer on the value of aesthesiometry (tactile sensitivity) as an objective measure of mental fatigue](https://dominiquemakowski.github.io/publication/nicolas2016can/nicolas2016can.pdf). *European Yearbook of the History of Psychology*, 2, 11-46.

Sperduti, M., **Makowski, D.**, & Piolino, P. (2016). [The protective role of long-term meditation on the decline of the executive component of attention in aging: a preliminary cross-sectional study](https://dominiquemakowski.github.io/publication/sperduti2016protective/sperduti2016protective.pdf). *Aging, Neuropsychology, and Cognition*, 23(6), 691-702.

\normalsize



# Communications

## General Audience / Media Coverage

\footnotesize

- Pint of Science, `r link('"Back to the Matrix : pilule bleue ou rouge ?"', "https://pintofscience.com/")`
. 16 May 2018, Paris, France.
- Public Debate, `r link("Art \\& science discussion on sensory illusions", "https://facts2017.u-bordeaux.fr/FESTIVAL/Programme/Agenda-2017/Rencards-du-savoir-Les-illusions-sensorielles.html")`. 24 November 2017, Bordeaux, France.
- Magazine, `r link("Neuroanatomie de la réalité : quand le réel n'est plus", "https://biblineuropsy.com/2016/04/19/les-yeux-brouilles/")`. 2016, Les yeux brouillés, 1, 48-55.
- National TV, `r link("The effect of violent images on the brain and body", "https://www.youtube.com/watch?v=ihGs1V9kz4w")`. 2015, Testé sous contrôle médical, France 4
- Online journal, `r link("”Avengers, l'ère d’Ultron” en 3D : aussitôt vu, aussitôt oublié ?", "(http://blog.francetvinfo.fr/actu-cine/2015/05/07/avengers-lere-dultron-en-3d-aussitot-vu-aussitot-oublie.html")`. 2015, francetvinfos.fr

\normalsize


## Talks

\tiny

<!-- \begin{center}\textit{2018}\end{center} -->

**Co-organizer** (2021). *La recherche aux temps de la COVID*, `r link("1ère journée du COllaborative COgnitive Science", "https://sites.google.com/view/les-cocos/")`, 29 November, Online.

**Makowski, D.**, Sperduti, M., Nicolas, S. & Piolino, P. (2018). *Interindividual Determinants of Emotion Regulation through Fiction*. 2ème Congrès Francophone de TCC, 14-16 June, Geneva, Switzerland.

**Makowski, D.** (2018, *invited*). *How Reality can Modulate Memory and Emotions*. CRPCPO's monthly seminar, 23 March, Amiens, France.

**Makowski, D.**, Sperduti, M., Nicolas, S. & Piolino, P. (2018). *Engagement in Fiction as an Altered State of Consciousness*. 6th Mind, Brain & Body Symposium, 15-16 March, Berlin, Germany.



<!-- \begin{center}\textit{2017}\end{center} -->

**Makowski, D.**, Sperduti, M., Nicolas, S. & Piolino, P. (2017). *Vers la thérapie neurocognitive ? L’apport des neurosciences affectives dans la TCC*. 45ème congrès de l’AFTCC, 14-16 December, Paris, France.

Sperduti, M., **Makowski, D.** & Piolino, P. (2017). *The Role of Self-Relevance and Interindividual Variability in Executive Functions in Implicit Emotion Regulation*. International Society for the Study of Interindividual Differences (ISSID), 24-28 July, Warsaw, Poland.

**Makowski, D.**, Sperduti, M. & Piolino, P. (2017). *The Distinctive Effect of Emotion Regulation andMindfulness on Attentional Capture*. 1ère Journée Scientifique des Jeunes Chercheurs du Centre de Recherches sur la Cognition et l’Apprentissage, 8 June, Poitiers, France.

<!-- \begin{center}\textit{2016}\end{center} -->

**Makowski, D.**, Sperduti, M. & Piolino, P. (2016).*”Being there” and Remembering it: Presence en-hances Encoding in Memory*. International Congress On Memory (ICOM), 17-22 July, Budapest, Hungary.

**Makowski, D.**, Sperduti, M. & Piolino, P. (2016). *The Sense of Reality as a feature of proto-Consciousness, its Alteration and Generation induced by Fictional Worlds*. Literary States of Consciousness, 2 June, Paris, France.

**Makowski, D.**, Sperduti, M. & Piolino, P. (2016). *Does Mindfulness ability differently affect Implicit and Explicit Emotion Regulation?* 2nd International Conference on Mindfulness (ICM), 11-15 May, Roma, Italy.

Sperduti, M., **Makowski, D.** & Piolino, P. (2016). *Does mindfulness enhance interoception? Dissociation between different interoceptive abilities*. 2nd International Conference on Mindfulness, 11-15 May, Roma, Italy.

<!-- \begin{center}\textit{2015}\end{center} -->

**Makowski, D.**, Sperduti, M. & Piolino, P. (2015). *Bon et Mauvais Régulateurs Emotionnels: Un Rôle Spécifique de l’Inhibition ?* 56è Congrès National de la Société Française de Psychologie (SFP), 2-4 September, Strasbourg, France.

**Makowski, D.**, Sperduti, M., Pelletier, J. & Piolino, P. (2015). *Régulation émotionnelle et Self Control : De la recherche Fondamentale à l’Application Clinique*. 1er Congrès Francophone de TCC, 27-29 May, Lyon, France.

<!-- \begin{center}\textit{2014}\end{center} -->

**Makowski, D.**, Sperduti, M., Arcangeli, M., Pelletier, J. & Piolino, P. (2014). *From Philosophy to the Rehabilitation of Psychiatric Patients: Fiction/Reality, Emotion et Cognitive Control*. Journée d’hiver de l’IUPDP, 19 December, Boulogne-Billancourt, France.

**Makowski, D.**, Sperduti, M. & Piolino, P. (2014). *L’émotion face à la fiction : l’étude de patients schizophrènes éclaire le paradoxe de la fiction*. 27 June, Fête de la Recherche, Boulogne-Billancourt,France.

<!-- \begin{center}\textit{2013}\end{center} -->

**Makowski, D.**, & Rossi, S. (2013). `r link("\\textit{Le jugement esthétique chez l’enfant}", "https://www.youtube.com/watch?v=Hvs7t5G_dLM")`. Journées Neurosciences, Esthétique, et Complexité, 28 September, Paris, France.


\normalsize

## Posters

\tiny

<!-- \begin{center}\textit{2021}\end{center} -->

Lau, Z. J., Pham, T., Boyce, W. P., Chen, S. A., & **Makowski, D.** (2021). `r link("\\textit{A Parametric Framework to Generate Visual Illusions using Python}", "https://youtu.be/uptP_NxEHaM")`. 43rd European Conference on Visual Perception, 22-27 Aug. Online.

<!-- \begin{center}\textit{2016}\end{center} -->

**Makowski, D.**, Sperduti, M. \& Piolino, P. (2016). *Régulation Emotionnelle, pleine-conscience et bien-être : Interactions et implication dans les troubles de l’humeur*. Journée d’hivers de la Société de Neuropsychologie de Langue Française, 5 December, Paris, France.

Blondé, P., Sperduti, M., **Makowski, D.** \& Piolino, P. (2016). *Le rôle des réseaux attentionnels sur l’encodage en mémoire épisodique dans le cadre du vieillissement et de sa variabilité interindividuelle liée aux traits de pleine conscience*. Journée d’hivers de la Société de Neuropsychologie de Langue Française, 5 December, Paris, France.

**Makowski, D.**, Sperduti, M. \& Piolino, P. (2016). 
*I know it’s not real... what does it change?* nCPN day, 16 September, Paris, France.

<!-- \begin{center}\textit{2015}\end{center} -->

**Makowski, D.**, Sperduti, M. \& Piolino, P. (2015). *"J’avais l’impression d’y être" : Sentiment de présence et encodage en mémoire autobiographique*. Journée d’hiver de la Société de Neuropsychologie de Langue Française, 5 December, Paris, France.

Sperduti, M., **Makowski, D.** \& Piolino, P. (2015). *Interaction entre systèmes attentionnels et encodage en mémoire épisodique*. Journée d’hivers de la Société de Neuropsychologie de Langue Française, 5 December, Paris, France.

**Makowski, D.**, Sperduti, M., Arcangeli, M., Pelletier, J. \& Piolino, P. (2015). *I know it’s not real... what does it change?* 12e colloque de la Société des Neurosciences, 19-22 May, Montpellier, France.

<!-- \begin{center}\textit{2014}\end{center} -->

**Makowski, D.**, Sperduti, M., Arcangeli, M., Pelletier, J. \& Piolino, P. (2014) *Emotion Regulation by fiction is related to cognitive inhibition.* Journée d’hiver de la Société de Neuropsychologie de Langue Française, 5 December, Paris, France.

Sperduti, M., **Makowski, D.**, Vialatte, F. \& Piolino, P. (2014). *The decline of Autobiographical Memory in aging, inhibition and the cingulate cortex: an activation and resting state fMRI study.* Journées d’Etudes du Vieillissement, 15-16 September, Caen, France.

Sperduti, M., **Makowski, D.** \& Piolino, P. (2014). *The protective role of meditation on the cognitive decline in aging: a cross-sectional study*. Journées d’Etudes du Vieillissement, 15-16 September, Caen, France.

<!-- \begin{center}\textit{2013}\end{center} -->

**Makowski, D.**, Sperduti, M., Arcangeli, M., Pelletier, J. \& Piolino, P. (2013). *QUID du paradoxe de l’émotion face à la fiction ? Nouvelles données physiologiques comparant la réponse émotionnelle à des scènes réelles ou fictionnelles*. Journées de l’IUPDP, 19 December, Boulogne-Billancourt, France.

\normalsize

# References

\small 

Do not hesitate to contact them of any inquiry.

- **Pr Annabel Chen** (Postdoc supervisor): AnnabelChen@ntu.edu.sg
- **Dr Marco Sperduti** (PhD mentor): marco.sperduti@parisdescartes.fr
- **Pr Pascale Piolino** (PhD cosupervisor): pascale.piolino@parisdescartes.fr
- **Pr Serge Nicolas** (PhD cosupervisor): serge.nicolas@parisdescartes.fr

\normalsize
