---
name: Dominique
surname: Makowski
profilepic: "./img/profile.png"
position: "Assistant Professor in Psychology"
qualifications: "PhD"
address: "University of Sussex, Brighton, UK"
# phone: +1 22 3333 4444
www: dominiquemakowski.github.io
email: "D.Makowski@sussex.ac.uk"
twitter: Dom_Makowski
github: DominiqueMakowski
# linkedin: dominiquemakowski
# orcid: "0000-0001-5375-9967"
aboutme: |
  \RaggedRight Trained as a clinical neuropsychologist, I am currently an assistant professor at the University of Sussex researching aspects of reality bending (e.g., illusions, beliefs of reality, neuroscience of deception, fake news, altered states of consciousness), the role of the body and emotions in cognition (e.g., emotion regulation and interoception), and methodology (statistics, programming, and neurophysiological techniques).
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "1976D2"
output:
  vitae::awesomecv:
    page_total: true
    keep_md: true
editor_options:
  chunk_output_type: console
header-includes:
  - \definecolor{cvlinkcolor}{HTML}{1976D2}
  - \hypersetup{colorlinks=true, urlcolor=cvlinkcolor, linkcolor=cvlinkcolor}
  - \usepackage{float}
  - \newcommand*{\subsubsectionstyle}[1]{{\fontsize{10pt}{1em}\bodyfont\itshape\color{graytext}{#1}}}
  - \renewcommand{\subsubsection}[1]{\par\vspace{\acvSectionContentTopSkip}\vspace{-1.5mm}\subsubsectionstyle{#1}\phantomsection}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(ggplot2)

link <- function(txt, url, color = "1976D2") {
  paste0("\\href{", url, "}{\\color[HTML]{", color, "}{", txt, "}}")
}
```

<!-- # Current Position -->

<!-- ```{r CurrentEmployment} -->
<!-- data <- tibble( -->
<!--   what = "Lecturer in Psychology", -->
<!--   when = "2023 - Present", -->
<!--   with = "University of Sussex", -->
<!--   where = "UK", -->
<!--   details = c( -->
<!--     paste( -->
<!--       "Full teaching service on courses such as Quantitative and Qualitative Methods." -->
<!--     ), -->
<!--     paste( -->
<!--       "Head of the ", -->
<!--        link("Reality Bending Lab", "https://realitybending.github.io/"), -->
<!--       " (ReBeL) where we study reality perception (e.g., neuroscience of deception, perception of fake news, altered states of consciousness), the role of the body and emotions in cognition (e.g., emotion regulation and interoception), and methodology (statistics, programming, open source software and neurophysiological techniques)." -->
<!--     ) -->
<!--   ) -->
<!-- ) -->

<!-- vitae::detailed_entries(data, with, when, what, where, details, .protect = FALSE) -->
<!-- ``` -->

<!-- \footnotesize -->

<!-- The NTU "presidential postdoc fellowship" is a competitive grant meant as an intermediate step between postdoc and faculty. While integrated within a larger lab (the [Clinical Brain Lab](https://www.clinicalbrain.org/), directed by Prof Annabel Chen), I am pursuing my own research track on the perception of reality, managing my team (3 research assistants, and several undergrad students) and research funding ($ 200k). I am involved in all the research and administrative aspects of the project (writing IRBs, project budgeting, experiment creations, data collection, analysis, manuscript writing, ...). -->

<!-- On top of the mentoring and teaching done in the context of the lab, I am also involved in university lectures (e.g., statistics for NTU students), research-oriented workshops (for instance, I have introduced our software *NeuroKit* at the OHBM conference this summer), and other courses (I have been recently appointed by the University of Zurich to give a 3 days course on Python to their PhD students). -->

\normalsize


# Education

```{r Education}
data <- rbind(tibble(
  what = "Doctor of Philosophy (PhD) - Psychology",
  when = "2014 - 18",
  with = "Université de Paris",
  where = "France",
  # details = NA
  details = paste0(
    "Thesis: Cognitive Neuropsychology of Implicit Emotion Regulation through Fictional Reappraisal (supervised by ",
    link("Pr Serge Nicolas", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Serge-Nicolas"),
    " \\& ",
    link("Pr Pascale Piolino", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Pascale-Piolino"),
    ")"
  )
), tibble(
  what = "Certified Psychotherapist - Cognitive Behavioural Therapy (CBT)",
  when = "2014 - 17",
  with = "French Association for Cognitive Behavioural Therapy (AFTCC)",
  where = "France",
  # details = NA
  details = c(
    "Thesis: Cognitive Behavioural Therapy for two Patients: One suffering from Motivation Disorder associated with Dysthymia and the other from Social Anxiety (supervised by Sophie Kindynis)"
  )
), tibble(
  what = "Master of Science (MSc) - Clinical Neuropsychology and Cognitive Psychology",
  when = "2012 - 14",
  with = "Université de Paris",
  where = "France",
  # details = NA
  details = c(
    paste0("Second year thesis: How the Study of Emotions in Schizophrenia enlight the Paradox of Fiction (supervised by ", link("Pr Pascale Piolino", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Pascale-Piolino"), ")"),
    paste0("First year thesis: The Cognitive Development of the Aesthetic Judgement in Children and Adults (supervised by ", link("Pr Sandrine Rossi", "https://www.researchgate.net/profile/Sandrine-Rossi"), ")")
  )
), tibble(
  what = "Bachelor of Science (BSc) - Psychology",
  when = "2009 - 12",
  with = "Université de Paris",
  where = "France",
  details = NA
))

vitae::detailed_entries(data, with, when, what, where, details, .protect = FALSE)
```


# Experience

## Research

```{r ExperienceResearch}
data <- rbind(
tibble(
  Position = "Assistant Professor (Current Position)",
  Date = "2023 - Present",
  Institution = "School of Psychology, University of Sussex",
  Where = "UK",
  Activity = c(
    paste(
      "Full teaching service on courses including Bayesian Statistics and Psychophysiology."
    ),
    paste(
      "Head of the ",
       link("Reality Bending Lab", "https://realitybending.github.io/"),
      " (ReBeL) where we study reality perception (e.g., neuroscience of deception, perception of fake news, altered states of consciousness), the role of the body and emotions in cognition (e.g., emotion regulation and interoception), and methodology (statistics, programming, open source software and neurophysiological techniques)."
    ),
    paste(
      "School-level leadership responsibilities, including research ethics, the research participation scheme and postgraduate programme development."
    )
  )),
tibble(
  Position = "Presidential Research Fellow",
  Date = "2021 - 22",
  Institution = "Clinical Brain Lab, Nanyang Technological University (NTU)",
  Where = "Singapore",
  Activity = paste0(
    'The NTU "presidential postdoc fellowship" is a competitive two-years grant meant as an intermediate step between postdoc and faculty. While integrated within a larger lab (the ',
    link("Clinical Brain Lab", "https://www.clinicalbrain.org/"),
    ', directed by ',
    link("Pr Annabel Chen", "https://www.clinicalbrain.org/author/annabel-chen/"),
    ', I am pursuing my own research track on the neurocognitive and affective processes underlying the beliefs in fake vs. real stimuli (fake news, fiction, ...), managing my team (3 research assistants, and several undergrad students) and research funding (\\$ 200k).'
  )),
tibble(
  Position = "Research Fellow",
  Date = "2019 - 20",
  Institution = "Clinical Brain Lab, Nanyang Technological University (NTU)",
  Where = "Singapore",
  Activity = paste0(
    "First postdoc position, working on a project funded by the ministry of defence about the neurocognitive correlates of deception. Responsible for studies design and completion, data analysis, publications and co-supervision of one PhD student, two research assistants and several graduate and undergraduate students (reference: ",
    link("Pr Annabel Chen", "https://www.clinicalbrain.org/author/annabel-chen/"),
    ")."
  )),
tibble(
  Position = "Research Assistant",
  Date = "2012",
  Institution = "Developmental Psychology Lab (LaPsyDé), Université de Paris",
  Where = "Paris, France",
  Activity = paste0(
    "Data collection for a study (",
    link("Borst, 2016", "http://psycnet.apa.org/journals/emo/13/5/811/"),
    ") on emotions and mental rotation (reference: ", link("Pr Grégoire Borst", "https://www.lapsyde.com/gregoire-borst"),
    ")."
  )),
tibble(
  Position = "Research Assistant",
  Date = "2011",
  Institution = "Memory \\& Cognition Lab (LMC), Université de Paris",
  Where = "Paris, France",
  Activity = paste0(
    "Experiment creation and data collection for a study on memory, salience and bizarreness effect (reference: ",
    link("Pr Serge Nicolas", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Serge-Nicolas"),
    ")."
  ))
)

# Save for re-useability
write.csv(data, "data/experience_research.csv", row.names = FALSE, fileEncoding = "UTF-8")

vitae::detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```

## Teaching

```{r ExperienceTeaching}
data <- rbind(
  tibble(
  Position = "Module convenor (Bayesian Statistics)",
  Date = "2024 - Present",
  Institution = "University of Sussex",
  Where = "Brighton, UK",
  Activity = "I teach the Bayesian framework and Bayesian modelling with brms (Master and PhD level)."
),tibble(
  Position = "Module teacher (Statistics)",
  Date = "2023 - Present",
  Institution = "University of Sussex",
  Where = "Brighton, UK",
  Activity = "I teach lectures and practicals on statistics with R (Bachelor and Master level)."
),tibble(
  Position = "Module teacher (Psychophysiology)",
  Date = "2023 - Present",
  Institution = "University of Sussex",
  Where = "Brighton, UK",
  Activity = "I teach lectures on Psychophysiology and Interoception in Cognitive Neuroscience modules (Bachelor and Master level)."
),tibble(
  Position = "Assistant Lecturer (Clinical Neuropsychology)",
  Date = "2017 - 18",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = paste0("Modules (192 h; bachelor \\& master students): Neurology and psychiatry (main neurodegenerative, neurological and psychiatric disorders), assessment (examination, diagnostic, psychometry), rehabilitation and psychotherapy (CBT, mindfulness-based therapies, cognitive rehabilitation, practice supervision), general neuroscience and psychology (neuroanatomy, emotion regulation...). Reference: ", link("Pr Isabelle Jambaqué", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Isabelle-Jambaque-Aubourg"), ".")
), tibble(
  Position = "Teaching Assistant (Differential Cognitive Psychology)",
  Date = "2015 - 17",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = "Modules (144 h; 1st \\& 2nd year students): Experimental methodology (assessment and related problems, scientific reasoning, psychometric properties of tests and questionnaires, statistics...) and introduction to concepts such as intelligence, personality and creativity. Reference: Dr Christophe Mouchiroud."
), tibble(
  Position = "Teaching Assistant (Cognitive Psychology)",
  Date = "2014 - 16",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = paste0("Modules (48 h; 3rd year students): Models of working memory, mental imagery and categorisation. Reference: ", link("Pr Todd Lubart", "https://lapea.recherche.parisdescartes.fr/membres-permanents/todd-lubart/"), ".")
# ), tibble(
#   Position = "Teaching Assistant (University Services)",
#   Date = "2013",
#   Institution = "Université de Paris",
#   Where = "Paris, France",
#   Activity = "Modules (16 h; 1st year students): Introduction to the use of internet (internet security, anonymity, etc.) and on-line university services for first year students. Reference: Dr Christian Fondrat."
))


# Save for re-useability
write.csv(data, "data/experience_teaching.csv", row.names = FALSE, fileEncoding = "UTF-8")

vitae::detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```


## Consultancy and Knowledge Exchange

### Instructor

```{r ConsultancyInstructor}
data <- rbind(
tibble(
  Position = "Contracted Instructor",
  Date = "2026",
  Institution = "South East Doctoral Training Arc (SEDarc)",
  Where = "UK",
  Activity = "Recording of a re-usable \\textit{Introduction to GitHub} lecture for PhD students across the SEDarc partnership of six UK universities."
),tibble(
  Position = "Invited Instructor (Psychophysiology)",
  Date = "2024",
  Institution = "University of Basel",
  Where = "Basel, Switzerland",
  Activity = paste0("Full-day workshop (8 h; PhD students): Recording, Analyzing and Using Physiological Signals in Psychology. Reference: ", link("Dr Dorothee Bentz", "https://psychologie.unibas.ch/de/personen/dorothee-bentz/"), ".")
),tibble(
  Position = "Invited Instructor (Bayesian Statistics)",
  Date = "2024",
  Institution = "Université de Paris",
  Where = "Paris, France",
  Activity = "Workshop on Bayesian statistics for the members of a research lab."
),tibble(
  Position = "Invited Instructor (Programming and Data Science)",
  Date = "2022",
  Institution = "University of Zurich",
  Where = "Zürich, Switzerland",
  Activity = paste0("Online workshop (24 h; PhD students): Advanced Python programming for signal processing and data analysis. Reference: ", link("Dr Maike Krannich", "https://www.psychologie.uzh.ch/de/studium/doktorat/team.html"), ".")
),tibble(
  Position = "Invited Instructor (Mixed Models)",
  Date = "2021",
  Institution = "Nanyang Technological University (NTU)",
  Where = "Singapore",
  Activity = "Workshop on mixed models in R."
)
)

vitae::detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```

### Developer

```{r ConsultancyDeveloper}
data <- tibble(
  Position = "Contracted Developer",
  Date = "2026",
  Institution = "Institute for Advanced Consciousness Studies",
  Where = NA,
  Activity = "Development of hyperscanning capabilities for an open-source portable EEG software."
)

vitae::detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```

### Contract Research

```{r ConsultancyResearch}
data <- tibble(
  Position = "Contract Research",
  Date = "2026",
  Institution = "Fragrance industry (client confidential)",
  Where = NA,
  Activity = "Contract research on the relationship between smells and emotions."
)

vitae::detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```


## Clinical

```{r ExperienceClinical}
data <- rbind(tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2013 - 14",
  Institution = "Department of adult psychiatry, Pitié-Salpêtrière Hospital",
  Where = "Paris, France",
  Activity = paste0("Neuropsychology internship (512 h) under ", link("Dr Séverine Hatif", "https://fr.linkedin.com/in/hatif-severine-032596157"), ". Assessment and diagnostic of psychiatric or neurological illnesses among adults, as well as development and application of cognitive rehabilitation programs.")
),tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2012 - 13",
  Institution = "Department of geriatric psychiatry, Sainte-Anne Hospital",
  Where = "Paris, France",
  Activity = "Neuropsychology internship (304 h) under Emmanuel Guiliano. Assessment and diagnostic of psychiatric and neurological illnesses among an elderly population."
),tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2012",
  Institution = "Department of gerontology, La Porte Verte Hospital",
  Where = "Versailles, France",
  Activity = "Neuropsychology internship (96 h) under Sophie Fleury. Observation of assessment and diagnostic of memory related deficits such as neurodegenerative diseases, somatic ageing-related illnesses or depression."
))


# Save for re-useability
write.csv(data, "data/experience_clinical.csv", row.names = FALSE, fileEncoding = "UTF-8")

vitae::detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```


# Software and Tools

\small

I develop and maintain open-source software and measurement tools used across psychological and neuroscientific research.

\normalsize


```{r SoftwareTools, echo=FALSE, results='asis'}
df <- rbind(
  data.frame(
    Name = "\\href{https://github.com/easystats/easystats}{\\textbf{easystats}}",
    Type = "Software",
    Description = "R packages for accessible statistical modelling (bayestestR, parameters, performance, modelbased, ...)"
  ),
  data.frame(
    Name = "\\href{https://github.com/neuropsychology/NeuroKit}{\\textbf{NeuroKit}}",
    Type = "Software",
    Description = "Python toolbox for neurophysiological signal processing"
  ),
  data.frame(
    Name = "\\href{https://github.com/realitybending/Pyllusion}{\\textbf{Pyllusion}}",
    Type = "Software",
    Description = "Python framework to generate visual illusions"
  ),
  data.frame(
    Name = "\\href{https://github.com/DominiqueMakowski/cogmod}{\\textbf{cogmod}}",
    Type = "Software",
    Description = "R package for Bayesian cognitive models of decision-making tasks"
  ),
  data.frame(
    Name = "\\href{https://github.com/neuropsychology/Neuropsydia.py}{\\textbf{Neuropsydia}}",
    Type = "Software",
    Description = "Python package for creating experiments"
  ),
    data.frame(
    Name = "\\href{https://doi.org/10.1038/s41598-023-33148-5}{\\textbf{Illusion Game}}",
    Type = "Measure",
    Description = "Parametric visual illusion task measuring illusion sensitivity"
  ),
  data.frame(
    Name = "\\href{https://link.springer.com/article/10.1007/s12144-021-01760-1}{\\textbf{Lie Scale}}",
    Type = "Measure",
    Description = "Self-report measure of lying styles and attitudes"
  ),
  data.frame(
    Name = "\\href{https://osf.io/preprints/psyarxiv/8qrht}{\\textbf{MINT Scale}}",
    Type = "Measure",
    Description = "Multimodal interoception questionnaire"
  )
)

# 1. Subset the dataframe by Type
soft_df <- df[df$Type == "Software", ]
quest_df <- df[df$Type == "Measure", ]

# 2. Find the max rows needed to ensure we don't drop data
max_rows <- max(nrow(soft_df), nrow(quest_df))

# 3. Extract columns and pad the shorter list with empty strings
soft_names <- c(soft_df$Name, rep("", max_rows - nrow(soft_df)))
soft_desc  <- c(soft_df$Description, rep("", max_rows - nrow(soft_df)))

quest_names <- c(quest_df$Name, rep("", max_rows - nrow(quest_df)))
quest_desc  <- c(quest_df$Description, rep("", max_rows - nrow(quest_df)))

# 4. Combine into exactly 4 columns
rows <- paste(soft_names, soft_desc, quest_names, quest_desc, sep = " & ")
body <- paste(rows, collapse = " \\\\\n")

# 5. Output the LaTeX
cat(
  "\\begin{table}[H]\n",
  "\\centering\n",
  "\\scriptsize\n",
  "\\begin{tabular}{p{0.085\\linewidth} p{0.39\\linewidth} p{0.11\\linewidth} p{0.365\\linewidth}}\n",
  # "\\toprule\n",
  "\\multicolumn{2}{c}{\\textbf{Software}} & \\multicolumn{2}{c}{\\textbf{Measure}} \\\\\n",
  "\\cmidrule(lr){1-2} \\cmidrule(lr){3-4}\n",
  body, " \\\\\n",
  # "\\bottomrule\n",
  "\\end{tabular}\n",
  "\\end{table}\n",
  sep = ""
)
```

\newpage

# Skills

## Language

```{r Language, message=FALSE, warning=FALSE, fig.align="left", fig.height=1.25*0.8, fig.width=4*0.7, dpi=300}
library(ggplot2)
library(patchwork)

## ---- Flags, drawn on a standardized 3x2 canvas ----

flag_stripes_vertical <- function(colors) {
  n <- length(colors); w <- 3 / n
  df <- data.frame(xmin = (0:(n-1)) * w, xmax = (1:n) * w,
                    ymin = 0, ymax = 2, fill = colors)
  ggplot(df) +
    geom_rect(aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=fill),
              color = "grey70", linewidth = 0.2) +
    scale_fill_identity() +
    coord_fixed(xlim = c(0,3), ylim = c(0,2), expand = FALSE)
}

flag_stripes_horizontal <- function(colors) {
  n <- length(colors); h <- 2 / n
  df <- data.frame(ymin = (0:(n-1)) * h, ymax = (1:n) * h,
                    xmin = 0, xmax = 3, fill = colors)
  ggplot(df) +
    geom_rect(aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=fill),
              color = "grey70", linewidth = 0.2) +
    scale_fill_identity() +
    coord_fixed(xlim = c(0,3), ylim = c(0,2), expand = FALSE)
}

flag_france  <- function() flag_stripes_vertical(c("#0055A4", "#FFFFFF", "#EF4135"))
flag_italy   <- function() flag_stripes_vertical(c("#009246", "#FFFFFF", "#CE2B37"))
flag_poland  <- function() flag_stripes_horizontal(c("#DC143C", "#FFFFFF"))  # red bottom, white top

flag_uk <- function() {
  ggplot() +
    geom_rect(aes(xmin=0, xmax=3, ymin=0, ymax=2), fill = "#00247D") +
    geom_polygon(aes(x=c(0,0.4,3,3,2.6,0), y=c(2,2,0.32,0,0,1.68)), fill = "white") +
    geom_polygon(aes(x=c(0,0.4,3,3,2.6,0), y=c(0,0,1.68,2,2,0.32)), fill = "white") +
    geom_polygon(aes(x=c(0,0.2,3,3,2.8,0), y=c(2,2,0.16,0,0,1.84)), fill = "#CF142B") +
    geom_polygon(aes(x=c(0,0.2,3,3,2.8,0), y=c(0,0,1.84,2,2,0.16)), fill = "#CF142B") +
    geom_rect(aes(xmin=1.3, xmax=1.7, ymin=0, ymax=2), fill = "white") +
    geom_rect(aes(xmin=0, xmax=3, ymin=0.75, ymax=1.25), fill = "white") +
    geom_rect(aes(xmin=1.42, xmax=1.58, ymin=0, ymax=2), fill = "#CF142B") +
    geom_rect(aes(xmin=0, xmax=3, ymin=0.87, ymax=1.13), fill = "#CF142B") +
    coord_fixed(xlim = c(0,3), ylim = c(0,2), expand = FALSE)
}

## ---- Panel: flag + border, title above, level below ----

flag_panel <- function(flag_plot, language, level_label) {
  flag_plot +
    geom_rect(aes(xmin=0, xmax=3, ymin=0, ymax=2), fill = NA,
              color = "grey60", linewidth = 0.3) +
    labs(title = language, caption = level_label) +
    theme_void() +
    theme(
      plot.title   = element_text(hjust = 0.5, size = 9, face = "bold", margin = margin(b = 6)),
      plot.caption = element_text(hjust = 0.5, size = 8, color = "grey40", margin = margin(t = 6)),
      plot.margin  = margin(4, 6, 4, 6)
    )
}

## ---- Assemble ----

langs <- list(
  list(language="French",  level="Native",        flag=flag_france()),
  list(language="Polish",  level="Native",        flag=flag_poland()),
  list(language="English", level="Fluent",        flag=flag_uk()),
  list(language="Italian", level="B1 (learning)", flag=flag_italy())
)

plots <- lapply(langs, function(l) flag_panel(l$flag, l$language, l$level))

p_languages <- wrap_plots(plots, nrow = 1)
# ggsave("img/languages.png", p_languages, width = 8, height = 1.8,
#        dpi = 300, bg = "transparent")
p_languages
```


## Techniques

\small

- **Bayesian Statistics**: Predictive and structural modelling within a Bayesian framework (Stan, brms), including custom distributional families and computational cognitive models.
- **Psychophysiology \& EEG**: Acquisition, preprocessing and analysis of EEG and physiological signals (ECG, EDA, HRV).
- **Computational Modelling**: Application of ML/deep learning and computational modelling to psychological and neuroscientific data.
- **Open Science**: Strong commitment to reproducible research practices, open data/code sharing, and sustained contribution to open-source software communities.

\normalsize




# Additional Training

## Teaching

```{r TrainingTeaching}
data <- rbind(tibble(
  what = "CITI Certification",
  when = "2019",
  with = "Collaborative Institutional Training Initiative (ethics and scientific integrity in research)",
  where = "Online",
  details = NA
), tibble(
  what = "Academic Teaching Certificate",
  when = "2017",
  with = "Université of Paris (40h training in pedagogy and innovative teaching)",
  where = "France",
  details = NA
))

vitae::detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```


## Clinical

```{r TrainingClinical}
data <- rbind(tibble(
  what = "Certified Hypnotherapist",
  when = "2019",
  with = "National Guild of Hypnotists (100h - Note that although trained and qualified, I do not endorse hypnosis)",
  where = "Singapore",
  instructor = "Fauziah Shah",
  details = NA
), tibble(
  what = "Mindfulness based on Compassion and Insight (MBCI)",
  when = "2016",
  with = "Institute for psychiatry, Sainte-Anne Hospital (16h master class)",
  instructor = "Pr Pascal Delamillieure",
  where = "France",
  details = NA
), tibble(
  what = "First Aid Certificate",
  when = "2016",
  with = "Université de Paris (16h - level 1)",
  where = "France",
  instructor = NA,
  details = NA
))

vitae::detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```

## Neuroimaging

```{r TrainingNeuroimaging}
data <- rbind(tibble(
  what = "Structural, Functional and Radiological Neuroanatomy",
  when = "2020",
  with = "Neurocourses UK (32h)",
  where = "Online",
  instructor = "Dr Paul Johns",
  details = NA
), tibble(
  what = "MRI Connectivity Analysis",
  when = "2015",
  with = "National Institute of Nuclear Sciences \\& Techniques - INSTN (32h)",
  where = "Marseille, France",
  instructor = "Dr Jorge L. Armony",
  details = NA
), tibble(
  what = "fMRI : Preprocessing and Analysis",
  when = "2014 - 15",
  with = "Sainte-Anne Hospital (32h)",
  where = "Paris, France",
  instructor = "Dr Sylvain Charron",
  details = NA
), tibble(
  what = "Signal Processing Theory and Application for EEG",
  when = "2014",
  with = "École Supérieure de Physique et de Chimie Industrielle - ESPCI (24h)",
  where = "Paris, France",
  instructor = "Dr François Vialatte",
  details = NA
))

vitae::detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```

## Statistics and Programming

```{r TrainingStatistics}
data <- rbind(tibble(
  what = "Creating Online Experiments in PsychoPy and Pavlovia",
  when = "2020",
  with = "University of Nottingham (24h)",
  where = "Online",
  instructor = "Dr Rebecca Hirst",
  details = NA
), tibble(
  what = "Scientific Programming with Python and Software Engineering Best Practices",
  when = "2016",
  with = "Telecom ParisTech (16h)",
  where = "Paris, France",
  instructor = "Dr Alexandre Gramfort",
  details = NA
), tibble(
  what = "P4N: Python for Neuroscience (and Psychology)",
  when = "2016",
  with = "University of Nottingham (24h)",
  where = "Nottingham, UK",
  instructor = "Dr Jon Peirce",
  details = NA
), tibble(
  what = "Machine Learning and Brain-to-Computer Interfaces",
  when = "2014",
  with = "École Supérieure de Physique et de Chimie Industrielle - ESPCI (16h)",
  where = "Paris, France",
  instructor = "Dr François Vialatte",
  details = NA
))

vitae::detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```


## Miscellaneous

```{r TrainingMisc}
data <- rbind(tibble(
  what = "History of Arts",
  when = "2017-- 18",
  with = "École du Louvre (74h)",
  where = "Paris, France",
  details = NA
))

vitae::detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```





# Research Track Record


## Scientific Impact


```{r ScientificImpactFigure, echo = FALSE, fig.height=3, fig.width=10, out.width="80%", fig.align="center"}
load("data/data_scholar.Rdata")
source("functions.R")

p <- plot_impact(data_scholar)
ggsave("img/scientific_impact.png", p, width=10, height=4)
p
```


```{r ScientificImpact, echo = FALSE}
get_stats(data_scholar) |>
  knitr::kable(
    col.names = c(
      "\\textit{n}-Publications \\textit{(total)}",
      "\\textit{n}-1\\textsuperscript{st} author",
      "\\textit{n}-2\\textsuperscript{nd} author",
      "\\textit{n}-Senior author",
      "H-index",
      "Citations \\textit{(total)}"
    ),
    format = "latex",
    booktabs = TRUE,
    escape = FALSE
  ) %>%
  kableExtra::kable_styling(position = "center", font_size = 8, latex_options = "hold_position")
```



## Grants


```{r Grants}
data <- rbind(
  tibble(
  Name = paste0(link("Centre for Open Science: Funding Consciousness Research with Registered Reports", "https://www.cos.io/blog/funding-consciousness-research", color = "333333"), " (PI)"),
  Details = "Consciousness Registered Reports: Illusion Sensitivity and Phenomenological
Control",
  Date = "2024 - 26",
  Amount = "\\$28,163",
  Activity = NA
),tibble(
  Name = paste0(link("TL@NTU's Behavioural and Communication Science Programme (BCSP) Grant", "https://www.ntu.edu.sg/temasek-labs/research-focus/programme", color = "333333"), " (co-PI)"),
  # Details = link("Cognitive, Neural and Social Factors involved in the Perception of Real vs. Fake Information", "https://fcl.ethz.ch/research/research-projects/NICE.html", color = "5D5D5D"),
  Details = "Cognitive, Neural and Social Factors involved in the Perception of Real vs. Fake Information",
  Date = "2022 - 25",
  Amount = "\\$915,427",
  Activity = NA
),tibble(
  Name = paste0(link("Singapore National Research Foundation's Intra-CREATE Grant", "https://researchgrant.gov.sg/Pages/GrantCallDetail.aspx?AXID=NRF2021-ITS008&CompanyCode=nrf", color = "333333"), " (co-PI)"),
  Details = link("A Neuroscientific investigation of the Interaction between Crowdedness and Environment typology (NICE)", "https://fcl.ethz.ch/research/research-projects/NICE.html", color = "5D5D5D"),
  Date = "2021 - 22",
  Amount = "\\$249,730",
  Activity = NA
),tibble(
  Name = paste0(link("NTU Presidential Postdoctoral Fellowship", "https://www.ntu.edu.sg/research/research-careers/presidential-postdoctoral-fellowship-(ppf)", color = "333333"), " (PI)"),
  Details = "'That's Fake News': Modulating the Neurocognitive Processes Underlying the Belief in Deceptive Information",
  Date = "2020 - 22",
  Amount = "\\$360,000",
  Activity = NA
# ),tibble(
#   Name = link("Ministerial PhD scholarship", "https://improvingpsych.org/mission/awards/", color = "333333") ,
#   Details = "Three years of PhD fully funded by the French Ministry of Research",
#   Date = "2014 - 17",
#   Amount = "€80,000",
#   Activity = NA
))

vitae::detailed_entries(data, Details, Amount, Name, Date, Activity, .protect = FALSE)
```

## Awards


```{r Awards}
data <- rbind(
  tibble(
  Name = link("Sussex School of Psychology 2024 Award Winner", "https://www.linkedin.com/posts/dominiquemakowski_realitybendinglab-activity-7241790839134257152-wjR6?utm_source=share&utm_medium=member_desktop", color = "333333"),
  Details = paste0("Outstanding Student Supervision"),
  Date = "2024",
  Amount = NA,
  Activity = NA
),tibble(
  Name = link("Mission Award (Society for the Improvement of Psychological Science - SIPS)", "https://improvingpsych.org/mission/awards/", color = "333333"),
  Details = paste0("Obtained for the ", link("NeuroKit", "https://en.wikipedia.org/wiki/NeuroKit", color = "5D5D5D"), " Python package"),
  Date = "2024",
  Amount = NA,
  Activity = NA
),tibble(
  Name = link("University of Sussex Research Culture 2024 Awards Winner", "https://www.linkedin.com/posts/university-of-sussex-school-of-psychology_congratulations-to-the-5-winners-and-6-shortlisted-activity-7209487987682721793-d4qm?utm_source=social_share_send&utm_medium=member_desktop_web&rcm=ACoAAAjTVisBfrVtfzPXFkBFwGtFJYejv2DfvSs", color = "333333"),
  Details = paste0("For engagement in Open Science"),
  Date = "2024",
  Amount = "£1,000",
  Activity = NA
),tibble(
  Name = link("Mission Award (Society for the Improvement of Psychological Science - SIPS)", "https://improvingpsych.org/mission/awards/", color = "333333"),
  Details = paste0("Obtained for the ", link("easystats", "https://en.wikipedia.org/wiki/Easystats", color = "5D5D5D"), " collection of R packages"),
  Date = "2023",
  Amount = NA,
  Activity = NA
),tibble(
  Name = link("Best Article Award (Psychonomic Society)", "https://www.psychonomic.org/page/2020BestArticleAwards", color = "333333") ,
  Details = paste0("Obtained for ", link("Makowski et al. (2019)", "https://dominiquemakowski.github.io/publication/makowski2019phenomenal/")),
  Date = "2020",
  Amount = "\\$1,000",
  Activity = NA
),tibble(
  Name = link("Commendation (Society for the Improvement of Psychological Science - SIPS)", "https://improvingpsych.org/mission/awards/", color = "333333") ,
  Details = paste0("Obtained for the bayestestR R package ", link("(Makowski et al., 2019)", "https://joss.theoj.org/papers/10.21105/joss.01541")),
  Date = "2020",
  Amount = NA,
  Activity = NA
))

vitae::detailed_entries(data, Details, Amount, Name, Date, Activity, .protect = FALSE)
```

## Student Awards

\small

My students are also consistently winning awards for their work in my lab.

\normalsize

```{r StudentAwards}
data <- rbind(
  tibble(
    Name = "SAGE Publications Prize for Outstanding Application of Statistical Methods",
    Details = "Awarded to Emma Benn (3rd year dissertation)",
    Date = "2026",
    Amount = NA,
    Activity = NA
  ), tibble(
    Name = "Junior Research Assistant (JRA)",
    Details = " Scholarship awarded to Oliver Collins",
    Date = "2026",
    Amount = NA,
    Activity = NA
  ), tibble(
    Name = "SoCoBio Summer Internship",
    Details = "Scholarship awarded to Eva Mala",
    Date = "2025",
    Amount = NA,
    Activity = NA
  ), tibble(
    Name = "Sussex Partnership NHS Foundation Trust Prize",
    Details = "Awarded to Sam Marine (3rd year dissertation) for highest project mark",
    Date = "2025",
    Amount = NA,
    Activity = NA
  ), tibble(
    Name = "Adam Weiler Impact Award",
    Details = "Awarded to Rob Dickinson (PhD student)",
    Date = "2024",
    Amount = NA,
    Activity = NA
  ), tibble(
    Name = "SoCoBio Summer Internship",
    Details = "Scholarship awarded to Gregory Heaney",
    Date = "2024",
    Amount = NA,
    Activity = NA
  ), tibble(
    Name = "Junior Research Assistant (JRA)",
    Details = "Scholarship awarded to Jing Xu",
    Date = "2023",
    Amount = NA,
    Activity = NA
  ), tibble(
    Name = "Junior Research Assistant (JRA)",
    Details = "Scholarship awarded to Auz Moore",
    Date = "2023",
    Amount = NA,
    Activity = NA
  )
)

vitae::detailed_entries(data, Details, Amount, Name, Date, Activity, .protect = FALSE)
```

## Editorial Responsibilities

```{r EditorialResponsabilities}
data <- rbind(tibble(
  Position = "Associate Editor",
  Where = link("Frontiers in Psychology: \\textit{Quantitative Psychology and Measurement}", "https://www.frontiersin.org/journals/all/sections/quantitative-psychology-and-measurement", color = "333333"),
  Date = "2020 - 2024",
  Location = NA,
  Activity = NA
),tibble(
  Position = "Regular Reviewer",
  Where = link("Journal of Open Source Software", "https://joss.theoj.org/", color = "333333"),
  Date = "2018 - present",
  Location = NA,
  Activity = NA
),tibble(
  Position = "Reviewer",
  Where = "Biological Psychiatry, Personality and Individual Differences, Scientific Reports, Acta Psychologica, ...",
  Date = "2017 - present",
  Location = NA,
  Activity = NA
))

# brief_entries(data, Where, Date, Position, .protect = FALSE)
vitae::detailed_entries(data, Where, Date, Position, Location, Activity, .protect = FALSE)
```

# Teaching Record


## Academic

\small


I have given academic lectures (total hours since 2014: **424**) on the following topics:

- **Bayesian Statistics**
   - Bayesian framework
   - Bayesian models with the *brms* R package
- **Signal Processing**
   - Bodily signals acquisition and preprocessing
   - Heart rate
   - Electrodermal activity
- **Psychophysiology and Interoception**
   - Embodied Cognition
   - Interoceptive Models
   - Psychophysiology
   - Heart rate variability
- **Neuropsychology** (*192 hours; 2nd year, 3rd year and master level*)
    - Clinical Neuropsychology \scriptsize(Neuropsychological syndromes; Neuropsychological examination and diagnostic; Cognitive rehabilitation; Clinical practice supervision; Neuropsychology in psychiatry)\normalsize
    - Cognitive Neuroscience \scriptsize(Neuroanatomy; Emotion Regulation; Mindfulness; Memory; Neuroimaging)\normalsize
- **Differential Psychology** (*144 hours; 1st year level*)
    - Hands-on Lectures \scriptsize(Experimental Methodology; Scientific Reasoning; Psychometric properties of tests and questionnaires; Introductory Statistics)\normalsize
    - Theory \scriptsize(Intelligence; Personality; Creativity)\normalsize
- **Cognitive Psychology** (*48 hours; 3rd year level*)
    - Working memory
    - Mental imagery and categorisation
- **Programming for Psychologists** (*24 hours*)
   - Python Programming
   - Experiment creation using Python
- **Open Science and Research Tools** (*MRes level workshops*)
   - Version control and collaboration with Git and GitHub
   - Agentic coding tools for research
- **Other** (*16 hours*): Internet; Research Ethics; Digital Rights

\normalsize



## Curriculum Development

- **MSc Advanced Computational Psychology** (*2026 - Present*). Development of a new postgraduate programme at the University of Sussex, covering its curriculum structure, module content and learning outcomes.
- **Bayesian Statistics** (*2024 - Present*). Designed a new module from scratch, taught at Master and PhD level.


## Supervision

I have mentored more than 7 full-time research assistants.

I have also co-supervised bachelor and master students for their research projects.



# Service and Leadership


## Institutional Service

```{r InstitutionalService}
data <- rbind(tibble(
  Position = "Academic Lead, Research Participation Scheme (SONA)",
  Where = "School of Psychology, University of Sussex",
  Date = "2025 - Present",
  Details = NA,
  Activity = c(
    paste(
      "Redesigned the credit allocation and study approval rules of the School's research participation scheme to make it fairer and more transparent for both students and researchers."
    ),
    paste(
      "Trialled changes aimed at increasing the educational value of participation for students while simultaneously improving data quality, including measures to address low-effort responding."
    )
  )
),tibble(
  Position = "Programme Developer, MSc Advanced Computational Psychology",
  Where = "School of Psychology, University of Sussex",
  Date = "2026 - Present",
  Details = NA,
  Activity = paste(
    "Development of a new postgraduate programme, including its curriculum structure, module content and learning outcomes."
  )
),tibble(
  Position = "Member, Cross-Schools Research Ethics Committee (C-REC)",
  Where = "University of Sussex",
  Date = "2023 - Present",
  Details = NA,
  Activity = NA
))

vitae::detailed_entries(data, Position, Date, Where, Details, Activity, .protect = FALSE)
```


## Open Science and Research Culture

```{r OpenScience}
data <- rbind(tibble(
  Position = "Organizer, MORSE Seminar Series",
  Where = link("Centre for Open Science and Research Reform", "https://www.sussex.ac.uk/research/centres/centre-for-open-science-and-research-reform/"),
  Date = "2024 - Present",
  Details = "University of Sussex",
  Activity = paste(
    "Member of the Centre, where I convene MORSE (Methods for Open and Reproducible Science), a seminar series on openness, reproducibility and replicability in psychological science."
  )
),tibble(
  Position = "Open Science Champion (invited debate)",
  Where = "British Neuroscience Association (BNA) Members' Meeting",
  Date = "2024",
  Details = NA,
  Activity = paste0(
    "Invited to argue the open science position in the meeting's interactive debate, ",
    "\\textit{A cultural revolution in sustainable neuroscience is needed more than a cultural revolution in open neuroscience now}, ",
    "alongside Dr Charlotte Rae (Sustainability Champion) and Hannah Hope (Wellcome)."
  )
))

vitae::detailed_entries(data, Position, Date, Where, Details, Activity, .protect = FALSE)
```


## Conference Organization

```{r ConferenceOrganization}
data <- tibble(
  Position = "Co-organizer, \\textit{Artificial Emotion} Symposium",
  Where = "ESCAN 2026, Sapienza University, Rome, Italy",
  Date = "2026",
  Details = NA,
  Activity = paste0(
    "\\textit{Artificial Emotion: Affective Responses and Interaction with Artificial Intelligence}: a four-talk symposium ",
    "on affective, physiological and neural responses to artificial intelligence, co-organised with Marco Sperduti ",
    "(Università di Roma Tor Vergata) for the meeting of the European Society for Cognitive and Affective Neuroscience."
  )
)

vitae::detailed_entries(data, Position, Date, Where, Details, Activity, .protect = FALSE)
```


## Earlier Service

```{r EarlierService}
data <- rbind(tibble(
  Position = "Elected Representative",
  Details = "Representation of the PhD students at the university level",
  Where = "ED261-3CH doctoral school",
  Date = "2016 - 18",
  Activity = NA
),tibble(
  Position = "Community Manager",
  Details = "Organization of seminars, local conferences and social events",
  Where = "Memory \\& Cognition Lab",
  Date = "2014 - 15",
  Activity = NA
),tibble(
  Position = "Active Member",
  Details = "Organization of social events for students",
  Where = "Student Association (BDE)",
  Date = "2009 - 12",
  Activity = NA
))

vitae::detailed_entries(data, Position, Date, Where, Details, Activity, .protect = FALSE)
```



# Publications

```{r, child=c('publications.Rmd')}
```


# References

\small

Do not hesitate to contact them of any inquiry.

- **Pr Annabel Chen** (Postdoc supervisor): AnnabelChen@ntu.edu.sg
- **Dr Marco Sperduti** (PhD mentor): marco.sperduti@parisdescartes.fr
- **Pr Pascale Piolino** (PhD cosupervisor): pascale.piolino@parisdescartes.fr
- **Pr Serge Nicolas** (PhD cosupervisor): serge.nicolas@parisdescartes.fr

\normalsize
