---
name: Dominique
surname: Makowski
profilepic: "./img/profile.png"
position: "Research Fellow"
qualifications: "PhD"
address: "Nanyang Technological University, Singapore"
# phone: +1 22 3333 4444
www: dominiquemakowski.github.io
email: "dom.makowski@gmail.com"
twitter: Dom_Makowski
github: DominiqueMakowski
# linkedin: dominiquemakowski
# orcid: "0000-0001-5375-9967"
aboutme: |
  Trained as neuropsychologist, I am currently a postdoc in Singapore researching aspects of reality bending (e.g., neuroscience of deception, perception of fake news, altered states of consciousness) and methodology (statistics and neurophysiology).
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "1976D2"
output: 
  vitae::awesomecv:
    page_total: true
    keep_md: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(ggplot2)

link <- function(txt, url, color = "1976D2") {
  paste0("\\href{", url, "}{\\color[HTML]{", color, "}{", txt, "}}")
}

short <- FALSE
```

# Current Position

```{r CurrentEmployment}
data <- tibble(
  what = "Presidential Postdoctoral Fellow",
  when = "2020 - Present",
  with = "Clinical Brain Lab, Nanyang Technological University (NTU)",
  where = "Singapore",
  details = c(
    paste(
      "The",  
      link("NTU Presidential Postdoc award", "https://www.ntu.edu.sg/research/research-careers/presidential-postdoctoral-fellowship-(ppf)"), 
      "funded two years of postdoc for my project about the neurocognitive and affective processes underlying the beliefs in fake vs. real material (e.g., fake news, fiction, etc.)."),
    paste(
      "Reference:", 
      link("Pr Annabel Chen", "https://www.clinicalbrain.org/author/annabel-chen/"))
  )
)

detailed_entries(data, with, when, what, where, details, .protect = FALSE)
```



# Education

```{r Education}
data <- rbind(tibble(
  what = "Doctor of Philosophy (PhD) - Psychology",
  when = "2014 - 18",
  with = "Université de Paris",
  where = "France",
  details = paste0(
    "Thesis: Cognitive Neuropsychology of Implicit Emotion Regulation through Fictional Reappraisal (supervised by ",
    link("Pr Serge Nicolas", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Serge-Nicolas"), 
    " \\& ", 
    link("Pr Pascale Piolino", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Pascale-Piolino"), 
    ")."
  )
), tibble(
  what = "Certified Psychotherapist - Cognitive Behavioural Therapy (CBT)",
  when = "2014 - 17",
  with = "French Association for Cognitive-Behavioural Therapy (AFTCC)",
  where = "France",
  details = c(
    "Thesis: Cognitive and Behavioural Therapy of two Patients: One suffering from Motivation Disorder associated with Dysthymia and the other from Social Anxiety (supervised by Sophie Kindynis)"
  )
), tibble(
  what = "Master of Science (MSc) - Neuropsychology and Cognitive Psychology",
  when = "2012 - 14",
  with = "Université de Paris",
  where = "France",
  details = c(
    paste0("Second year thesis: How the Study of Emotions in Schizophrenia enlight the Paradox of Fiction (supervised by ", link("Pr Pascale Piolino", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Pascale-Piolino"), ")."),
    paste0("First year thesis: The Cognitive Development of the Aesthetic Judgement in Children and Adults (supervised ", link("Pr Sandrine Rossi", "https://www.researchgate.net/profile/Sandrine-Rossi"), ").")
  )
), tibble(
  what = "Bachelor of Arts (BA) - Psychology",
  when = "2009 - 12",
  with = "Université de Paris",
  where = "France",
  details = NA
))

if(short) {
  data <- data[1:3, ]
  data$details <- NA
}

detailed_entries(data, with, when, what, where, details, .protect = FALSE)
```

# Additional Training

<!-- \tiny -->
<!-- \emph{All the courses mentioned below were accredited or completion-certified.} -->
<!-- \normalsize -->


## Teaching

```{r TrainingTeaching}
data <- rbind(tibble(
  what = "CITI Certification",
  when = "2019",
  with = "Collaborative Institutional Training Initiative (ethics and scientific integrity in research)",
  where = "Online",
  details = NA
),tibble(
  what = "Academic Teaching Certificate",
  when = "2017",
  with = "Université of Paris (40h training in pedagogy and innovative teaching)",
  where = "France",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```


## Clinical

```{r TrainingClinical}
data <- rbind(tibble(
  what = "Certified Hypnotherapist",
  when = "2019",
  with = "National Guild of Hypnotists (100h - Note that although trained and qualified, I do not endorse hypnosis)",
  where = "Singapore",
  details = NA
),tibble(
  what = "Mindfulness based on Compassion and Insight (MBCI)",
  when = "2016",
  with = "Institute for psychiatry, Sainte-Anne Hospital (16h master class)",
  where = "France",
  details = NA
),tibble(
  what = "First Aid Certificate",
  when = "2016",
  with = "Université de Paris (16h - level 1)",
  where = "France",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```

## Neuroimaging

```{r TrainingNeuroimaging}
data <- rbind(tibble(
  what = "Structural, Functional and Radiological Neuroanatomy",
  when = "2020",
  with = "Neurocourses UK (32h)",
  where = "Online",
  instructor = "Dr Paul Johns",
  details = NA
),tibble(
  what = "MRI Connectivity Analysis",
  when = "2015",
  with = "National Institute of Nuclear Sciences \\& Techniques - INSTN (32h)",
  where = "Marseille, France",
  instructor = "Dr Jorge L. Armony",
  details = NA
),tibble(
  what = "fMRI : Preprocessing and Analysis",
  when = "2014 - 15",
  with = "Sainte-Anne Hospital (32h)",
  where = "Paris, France",
  instructor = "Dr Sylvain Charron",
  details = NA
),tibble(
  what = "Signal Processing Theory and Application for EEG",
  when = "2014",
  with = "École Supérieure de Physique et de Chimie Industrielle - ESPCI (24h)",
  where = "Paris, France",
  instructor = "Dr François Vialatte",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```

## Statistics and Programming

```{r TrainingStatistics}
data <- rbind(tibble(
  what = "Creating Online Experiments in PsychoPy and Pavlovia",
  when = "2020",
  with = "University of Nottingham (24h)",
  where = "Online",
  instructor = "Dr Rebecca Hirst",
  details = NA
),tibble(
  what = "Scientific Programming with Python and Software Engineering Best Practices",
  when = "2016",
  with = "Telecom ParisTech (16h)",
  where = "Paris, France",
  instructor = "Dr Alexandre Gramfort",
  details = NA
),tibble(
  what = "P4N: Python for Neuroscience (and Psychology)",
  when = "2016",
  with = "University of Nottingham (24h)",
  where = "Nottingham, UK",
  instructor = "Dr Jon Peirce",
  details = NA
),tibble(
  what = "Machine Learning and Brain-to-Computer Interfaces",
  when = "2014",
  with = "École Supérieure de Physique et de Chimie Industrielle - ESPCI (16h)",
  where = "Paris, France",
  instructor = "Dr François Vialatte",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```


## Miscellaneous

```{r TrainingMisc}
data <- rbind(tibble(
  what = "History of Arts",
  when = "2017-- 18",
  with = "École du Louvre (74h)",
  where = "Paris, France",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```


# Experience

## Research

```{r ExperienceResearch}
data <- rbind(tibble(
  Position = "Research Fellow",
  Date = "2019 - 20",
  Institution = "Clinical Brain Lab, Nanyang Technological University (NTU)",
  Where = "Singapore",
  Activity = paste0(
    "First postdoc position, working on a project funded by the ministry of defence about the neurocognitive correlates of deception. Responsible for studies design and completion, data analysis, publications and co-supervision of one PhD student, two research assistants and several graduate and undergraduate students (reference: ", 
    link("Pr Annabel Chen", "https://www.clinicalbrain.org/author/annabel-chen/"),
    ")."
  )
), tibble(
  Position = "Internship",
  Date = "2012",
  Institution = "Developmental Psychology Lab (LaPsyDé), Université de Paris",
  Where = "France",
  Activity = paste0(
    "Data collection for a study ", 
    link("(Borst, 2016)", "http://psycnet.apa.org/journals/emo/13/5/811/"),
    " on emotions and mental rotation (reference: ", link("Pr Grégoire Borst", "https://www.lapsyde.com/gregoire-borst"),
    ")."
  )
), tibble(
  Position = "Internship",
  Date = "2011",
  Institution = "Memory \\& Cognition Lab (LMC), Université de Paris",
  Where = "France",
  Activity = paste0(
    "Experiment creation and data collection for a study on memory, salience and bizarreness effect (reference: ",
    link("Pr Serge Nicolas", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Serge-Nicolas"),
    ")."
  )
))

if(short) {
  data <- data[1:1, ]
}

# Save for re-useability
write.csv(data, "data/experience_research.csv", row.names = FALSE)

detailed_entries(data, Position, Date, Institution, Where, Activity, .protect = FALSE)
```



# Skills

## Language

- **French**: Native
- **Polish**: Native
- **English**: Fluent
- **Italian**: B1 level (currently learning)

# Research Track Record

## Awards

## Editorial Responsibilities

## Scientific Impact

```{r ScientificImpact, echo = FALSE}
load("data/data_scholar.Rdata")
source("https://raw.githubusercontent.com/DominiqueMakowski/CV/main/functions.R")

get_stats(data_scholar) |> 
  knitr::kable(col.names = c("n Publications", "n 1st-author", "n 2nd-author", "n Last-author", "H-index", "Citations"),
               format = "latex",
               booktabs = TRUE) %>%
  kableExtra::kable_styling(position = "center")
```

```{r ScientificImpactFigure, echo = FALSE, fig.height=3, fig.width=10, out.width="100%"}
plot_impact(data_scholar)
```


# Publications

## Reality Manipulation


