---
name: Dominique
surname: Makowski
profilepic: "./img/profile.png"
position: "Research Fellow"
qualifications: "PhD"
address: "Nanyang Technological University, Singapore"
# phone: +1 22 3333 4444
www: dominiquemakowski.github.io
email: "dom.makowski@gmail.com"
twitter: Dom_Makowski
github: DominiqueMakowski
# linkedin: dominiquemakowski
# orcid: "0000-0001-5375-9967"
aboutme: |
  Trained as neuropsychologist, I am currently a postdoc in Singapore researching aspects of reality bending (e.g., neuroscience of deception, perception of fake news, altered states of consciousness) and methodology (statistics and neurophysiology).
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "1976D2"
output: 
  vitae::awesomecv:
    page_total: true
    keep_md: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(ggplot2)

link <- function(txt, url, color = "1976D2") {
  paste0("\\href{", url, "}{\\color[HTML]{", color, "}{", txt, "}}")
}

short <- FALSE
```

# Current Position

```{r CurrentEmployment}
data <- tibble(
  what = "Presidential Postdoctoral Fellow",
  when = "2020 - Present",
  with = "Clinical Brain Lab, Nanyang Technological University (NTU)",
  where = "Singapore",
  details = c(
    paste(
      "The",
      link("NTU Presidential Postdoc award", "https://www.ntu.edu.sg/research/research-careers/presidential-postdoctoral-fellowship-(ppf)"),
      "funded two years of postdoc for my project about the neurocognitive and affective processes underlying the beliefs in fake vs. real material (e.g., fake news, fiction, etc.)."
    ),
    paste(
      "Reference:",
      link("Pr Annabel Chen", "https://www.clinicalbrain.org/author/annabel-chen/")
    )
  )
)

detailed_entries(data, with, when, what, where, details, .protect = FALSE)
```



# Education

```{r Education}
data <- rbind(tibble(
  what = "Doctor of Philosophy (PhD) - Psychology",
  when = "2014 - 18",
  with = "Université de Paris",
  where = "France",
  details = paste0(
    "Thesis: Cognitive Neuropsychology of Implicit Emotion Regulation through Fictional Reappraisal (supervised by ",
    link("Pr Serge Nicolas", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Serge-Nicolas"),
    " \\& ",
    link("Pr Pascale Piolino", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Pascale-Piolino"),
    ")."
  )
), tibble(
  what = "Certified Psychotherapist - Cognitive Behavioural Therapy (CBT)",
  when = "2014 - 17",
  with = "French Association for Cognitive-Behavioural Therapy (AFTCC)",
  where = "France",
  details = c(
    "Thesis: Cognitive and Behavioural Therapy of two Patients: One suffering from Motivation Disorder associated with Dysthymia and the other from Social Anxiety (supervised by Sophie Kindynis)"
  )
), tibble(
  what = "Master of Science (MSc) - Neuropsychology and Cognitive Psychology",
  when = "2012 - 14",
  with = "Université de Paris",
  where = "France",
  details = c(
    paste0("Second year thesis: How the Study of Emotions in Schizophrenia enlight the Paradox of Fiction (supervised by ", link("Pr Pascale Piolino", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Pascale-Piolino"), ")."),
    paste0("First year thesis: The Cognitive Development of the Aesthetic Judgement in Children and Adults (supervised ", link("Pr Sandrine Rossi", "https://www.researchgate.net/profile/Sandrine-Rossi"), ").")
  )
), tibble(
  what = "Bachelor of Arts (BA) - Psychology",
  when = "2009 - 12",
  with = "Université de Paris",
  where = "France",
  details = NA
))

if (short) {
  data <- data[1:3, ]
  data$details <- NA
}

detailed_entries(data, with, when, what, where, details, .protect = FALSE)
```

# Additional Training

<!-- \tiny -->
<!-- \emph{All the courses mentioned below were accredited or completion-certified.} -->
<!-- \normalsize -->


## Teaching

```{r TrainingTeaching}
data <- rbind(tibble(
  what = "CITI Certification",
  when = "2019",
  with = "Collaborative Institutional Training Initiative (ethics and scientific integrity in research)",
  where = "Online",
  details = NA
), tibble(
  what = "Academic Teaching Certificate",
  when = "2017",
  with = "Université of Paris (40h training in pedagogy and innovative teaching)",
  where = "France",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```


## Clinical

```{r TrainingClinical}
data <- rbind(tibble(
  what = "Certified Hypnotherapist",
  when = "2019",
  with = "National Guild of Hypnotists (100h - Note that although trained and qualified, I do not endorse hypnosis)",
  where = "Singapore",
  details = NA
), tibble(
  what = "Mindfulness based on Compassion and Insight (MBCI)",
  when = "2016",
  with = "Institute for psychiatry, Sainte-Anne Hospital (16h master class)",
  where = "France",
  details = NA
), tibble(
  what = "First Aid Certificate",
  when = "2016",
  with = "Université de Paris (16h - level 1)",
  where = "France",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```

## Neuroimaging

```{r TrainingNeuroimaging}
data <- rbind(tibble(
  what = "Structural, Functional and Radiological Neuroanatomy",
  when = "2020",
  with = "Neurocourses UK (32h)",
  where = "Online",
  instructor = "Dr Paul Johns",
  details = NA
), tibble(
  what = "MRI Connectivity Analysis",
  when = "2015",
  with = "National Institute of Nuclear Sciences \\& Techniques - INSTN (32h)",
  where = "Marseille, France",
  instructor = "Dr Jorge L. Armony",
  details = NA
), tibble(
  what = "fMRI : Preprocessing and Analysis",
  when = "2014 - 15",
  with = "Sainte-Anne Hospital (32h)",
  where = "Paris, France",
  instructor = "Dr Sylvain Charron",
  details = NA
), tibble(
  what = "Signal Processing Theory and Application for EEG",
  when = "2014",
  with = "École Supérieure de Physique et de Chimie Industrielle - ESPCI (24h)",
  where = "Paris, France",
  instructor = "Dr François Vialatte",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```

## Statistics and Programming

```{r TrainingStatistics}
data <- rbind(tibble(
  what = "Creating Online Experiments in PsychoPy and Pavlovia",
  when = "2020",
  with = "University of Nottingham (24h)",
  where = "Online",
  instructor = "Dr Rebecca Hirst",
  details = NA
), tibble(
  what = "Scientific Programming with Python and Software Engineering Best Practices",
  when = "2016",
  with = "Telecom ParisTech (16h)",
  where = "Paris, France",
  instructor = "Dr Alexandre Gramfort",
  details = NA
), tibble(
  what = "P4N: Python for Neuroscience (and Psychology)",
  when = "2016",
  with = "University of Nottingham (24h)",
  where = "Nottingham, UK",
  instructor = "Dr Jon Peirce",
  details = NA
), tibble(
  what = "Machine Learning and Brain-to-Computer Interfaces",
  when = "2014",
  with = "École Supérieure de Physique et de Chimie Industrielle - ESPCI (16h)",
  where = "Paris, France",
  instructor = "Dr François Vialatte",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```


## Miscellaneous

```{r TrainingMisc}
data <- rbind(tibble(
  what = "History of Arts",
  when = "2017-- 18",
  with = "École du Louvre (74h)",
  where = "Paris, France",
  details = NA
))

detailed_entries(data, with, when, what, where, why = details, .protect = FALSE)
```




# Skills

## Language

- **French**: Native
- **Polish**: Native
- **English**: Fluent
- **Italian**: B1 level (currently learning)


## Neuroimaging

## Programming

Some of my main software include ... 

## Open Science and Reproducibility

Involved in open-science. 

Active in open-software communities to help users to answer technical and methodological questions.



# Research Track Record

## Grants and Awards


```{r GrantsAwards}
data <- rbind(tibble(
  Name = link("Singapore National Research Foundation's Intra-CREATE Grant (co-PI)", "https://researchgrant.gov.sg/Pages/GrantCallDetail.aspx?AXID=NRF2021-ITS008&CompanyCode=nrf", color = "333333"),
  Details = link("A Neuroscientific investigation of the Interaction between Crowdedness and Environment typology (NICE)", "https://fcl.ethz.ch/research/research-projects/NICE.html", color = "5D5D5D"),
  Date = "2021 - 22",
  Amount = "\\$249,730",
  Activity = NA
),tibble(
  Name = link("NTU Presidential Postdoctoral Fellowship", "https://www.ntu.edu.sg/research/research-careers/presidential-postdoctoral-fellowship-(ppf)", color = "333333"),
  Details = "'That's Fake News': Modulating the Neurocognitive Processes Underlying the Belief in Deceptive Information",
  Date = "2020 - 22",
  Amount = "\\$360,000",
  Activity = NA
),tibble(
  Name = link("Best Article Award (Psychonomic Society)", "https://www.psychonomic.org/page/2020BestArticleAwards", color = "333333") ,
  Details = paste0("Obtained for ", link("Makowski et al. (2019)", "https://dominiquemakowski.github.io/publication/makowski2019phenomenal/")),
  Date = "2020",
  Amount = "\\$1,000",
  Activity = NA
),tibble(
  Name = link("Commendation (Society for the Improvement of Psychological Science - SIPS)", "https://improvingpsych.org/mission/awards/", color = "333333") ,
  Details = paste0("Obtained for the bayestestR R package ", link("(Makowski et al., 2019)", "https://joss.theoj.org/papers/10.21105/joss.01541")),
  Date = "2020",
  Amount = "N/A",
  Activity = NA
),tibble(
  Name = link("Ministerial PhD scholarship", "https://improvingpsych.org/mission/awards/", color = "333333") ,
  Details = "Three years of PhD fully funded by the French Ministry of Research",
  Date = "2014 - 17",
  Amount = "€80,000",
  Activity = NA
))

detailed_entries(data, Details, Date, Name, Amount, Activity, .protect = FALSE)
```


## Editorial Responsibilities


```{r EditorialResponsabilities}
data <- rbind(tibble(
  Position = "Associate Editor",
  Where = link("Frontiers in Psychology: \\textit{Quantitative Psychology and Measurement}", "https://www.frontiersin.org/journals/all/sections/quantitative-psychology-and-measurement", color = "333333"),
  Date = "2020 - present",
  Activity = NA
),tibble(
  Position = "Regular Reviewer",
  Where = link("Journal of Open Source Software", "https://joss.theoj.org/", color = "333333"),
  Date = "2018 - present",
  Activity = NA
),tibble(
  Position = "Reviewer",
  Where = "\\color[HTML]{333333}{Biological Psychiatry, Personality and Individual Differences, Scientific Reports, Acta Psychologica, ...}",
  Date = "2017 - present",
  Activity = NA
))

brief_entries(data, Where, Date, Position, .protect = FALSE)
# detailed_entries(data, Where, Date, Position, Amount, Activity, .protect = FALSE)
```

## Scientific Impact


```{r ScientificImpactFigure, echo = FALSE, fig.height=3, fig.width=10, out.width="100%"}
load("data/data_scholar.Rdata")
source("https://raw.githubusercontent.com/DominiqueMakowski/CV/main/functions.R")

plot_impact(data_scholar)
```


```{r ScientificImpact, echo = FALSE}
get_stats(data_scholar) |>
  knitr::kable(
    col.names = c(
      "\\textit{n}-Publications \\textit{(total)}",
      "\\textit{n}-1\\textsuperscript{st} author",
      "\\textit{n}-2\\textsuperscript{nd} author",
      "\\textit{n}-Senior author",
      "H-index",
      "Citations \\textit{(total)}"
    ),
    format = "latex",
    booktabs = TRUE,
    escape = FALSE
  ) %>%
  kableExtra::kable_styling(position = "center", font_size = 8, latex_options = "hold_position")
```


# Teaching Record


## Academic

I have given academic lectures (total hours since 2014: **400**) on the following topics:

- **Neuropsychology** (*192 hours; 2nd year, 3rd year and master level*)
    - Clinical Neuropsychology \scriptsize(Neuropsychological syndromes; Neuropsychological examination and diagnostic; Cognitive rehabilitation; Clinical practice supervision; Neuropsychology in psychiatry)\normalsize
    - Cognitive Neuroscience \scriptsize(Neuroanatomy; Emotion Regulation; Mindfulness; Memory; Neuroimaging)\normalsize
- **Differential Psychology** (*144 hours; 1st year level*)
    - Hands-on Lectures \scriptsize(Experimental Methodology; Scientific Reasoning; Psychometric properties of tests and questionnaires; Introductory Statistics)\normalsize
    - Theory \scriptsize(Intelligence; Personality; Creativity)\normalsize
- **Cognitive Psychology** (*48 hours; 3rd year level*):
    - Working memory
    - Mental imagery and categorisation
- **Other** (*16 hours*): Internet; Research Ethics; Digital Rights


## Technical

I have performed several technical trainings and courses on topics like:

- Statistics using R
- Experiment creation using Python
- How to acquire electrophysiological (EDA, ECG, EMG) signal using *BIOPAC* and *AcqKnowledge®*
- How to ask and handle sensitive personal information about patients or participants


# Experience

## Research

```{r ExperienceResearch}
data <- rbind(tibble(
  Position = "Research Fellow",
  Date = "2019 - 20",
  Institution = "Clinical Brain Lab, Nanyang Technological University (NTU)",
  Where = "Singapore",
  Activity = paste0(
    "First postdoc position, working on a project funded by the ministry of defence about the neurocognitive correlates of deception. Responsible for studies design and completion, data analysis, publications and co-supervision of one PhD student, two research assistants and several graduate and undergraduate students (reference: ",
    link("Pr Annabel Chen", "https://www.clinicalbrain.org/author/annabel-chen/"),
    ")."
  )
), tibble(
  Position = "Research Assistant",
  Date = "2012",
  Institution = "Developmental Psychology Lab (LaPsyDé), Université de Paris",
  Where = "Paris, France",
  Activity = paste0(
    "Data collection for a study ",
    link("(Borst, 2016)", "http://psycnet.apa.org/journals/emo/13/5/811/"),
    " on emotions and mental rotation (reference: ", link("Pr Grégoire Borst", "https://www.lapsyde.com/gregoire-borst"),
    ")."
  )
), tibble(
  Position = "Research Assistant",
  Date = "2011",
  Institution = "Memory \\& Cognition Lab (LMC), Université de Paris",
  Where = "Paris, France",
  Activity = paste0(
    "Experiment creation and data collection for a study on memory, salience and bizarreness effect (reference: ",
    link("Pr Serge Nicolas", "http://recherche.parisdescartes.fr/LaboratoireMemoireCognition/Membres/Enseignants-Chercheurs/Serge-Nicolas"),
    ")."
  )
))

if (short) {
  data <- data[1:1, ]
}

# Save for re-useability
write.csv(data, "data/experience_research.csv", row.names = FALSE)

detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```


## Clinical

```{r ExperienceClinical}
data <- rbind(tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2013 - 14",
  Institution = "Department of adult psychiatry, Pitié-Salpêtrière Hospital",
  Where = "Paris, France",
  Activity = "Neuropsychology internship (512 h) under Dr Séverine Hatif. Assessment and diagnostic of psychiatric or neurological illnesses among adults, as well as development and application of cognitive rehabilitation programs."
),tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2012 - 13",
  Institution = "Department of geriatric psychiatry, Sainte-Anne Hospital",
  Where = "Paris, France",
  Activity = "Neuropsychology internship (304 h) under Emmanuel Guiliano. Assessment and diagnostic of psychiatric and neurological illnesses among an elderly population."
),tibble(
  Position = "Assistant Neuropsychologist",
  Date = "2012",
  Institution = "Department of gerontology, La Porte Verte Hospital",
  Where = "Versailles, France",
  Activity = "Neuropsychology internship (96 h) under Sophie Fleury. Observation of assessment and diagnostic of memory related deficits such as neurodegenerative diseases, somatic ageing-related illnesses or depression."
))


# Save for re-useability
write.csv(data, "data/experience_clinical.csv", row.names = FALSE)

detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```

## Teaching


```{r ExperienceTeaching}
data <- rbind(tibble(
  Position = "Lecturer (Clinical Neuropsychology)",
  Date = "2017 - 18",
  Institution = "Université de Paris (under Pr Isabelle Jambaqué)",
  Where = "Paris, France",
  Activity = "Courses (192 h; bachelor \\& master students): Neurology and psychiatry (main neurodegenerative, neurological and psychiatric disorders), assessment (examination, diagnostic, psychometry), rehabilitation and psychotherapy (CBT, mindfulness-based therapies, cognitive rehabilitation, practice supervision), general neuroscience and psychology (neuroanatomy, emotion regulation...)."
),tibble(
  Position = "Teaching Assistant (Differential Cognitive Psychology)",
  Date = "2015 - 17",
  Institution = "Université de Paris (under Dr Christophe Mouchiroud)",
  Where = "Paris, France",
  Activity = "Courses (144 h; 1st \\& 2nd year students): Experimental methodology (assessment and related problems, scientific reasoning, psychometric properties of tests and questionnaires, statistics...) and introduction to concepts such as intelligence, personality and creativity."
),tibble(
  Position = "Teaching Assistant (Cognitive Psychology)",
  Date = "2014 - 16",
  Institution = "Université de Paris",
  Where = "Versailles, France",
  Activity = c("Courses: Neurology and psychiatry (main neurodegenerative, neurological and psychiatric disorders), assessment (examination, diagnostic, psychometry), rehabilitation and psychotherapy (CBT, mindfulness-based therapies, cognitive rehabilitation, practice supervision), general neuroscience and psychology (neuroanatomy, emotion regulation...).",
               "Supervisor: Pr Isabelle Jambaqué")
))


# Save for re-useability
write.csv(data, "data/experience_clinical.csv", row.names = FALSE)

detailed_entries(data, Institution, Date, Position, Where, Activity, .protect = FALSE)
```

# Publications

## Reality Manipulation


# References

- **Prof. Annabel Chen** (Postdoc supervisor): AnnabelChen@ntu.edu.sg
- **Dr. Marco Sperduti** (PhD mentor): marco.sperduti@parisdescartes.fr
- **Prof. Pascale Piolino** (PhD cosupervisor): pascale.piolino@parisdescartes.fr
- **Prof. Serge Nicolas** (PhD cosupervisor): serge.nicolas@parisdescartes.fr
