---
name: Dominique
surname: Makowski
profilepic: "./img/profile.png"
position: "Research Fellow"
qualifications: "PhD"
address: "Nanyang Technological University, Singapore"
# phone: +1 22 3333 4444
www: dominiquemakowski.github.io
email: "dom.makowski@gmail.com"
twitter: Dom_Makowski
github: DominiqueMakowski
# linkedin: dominiquemakowski
# orcid: "0000-0001-5375-9967"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "1976D2"
output:
  vitae::awesomecv:
    page_total: true
    keep_md: true
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(ggplot2)

link <- function(txt, url, color = "1976D2") {
  paste0("\\href{", url, "}{\\color[HTML]{", color, "}{", txt, "}}")
}

short <- FALSE
```

# Selected Publications

\small

**Makowski, D.**, Pham, T., Lau, Z. J., Brammer, J. C., Lespinasse, F., Pham, H., Schötzel, C., & Chen, S. A. (2021). [NeuroKit2: A Python Toolbox for Neurophysiological Signal Processing](https://dominiquemakowski.github.io/publication/makowski2021neurokit/makowski2021neurokit.pdf). *Behavior Research Methods*, 1-8.

**Makowski, D.**, Sperduti, M., Pelletier, J., Blondé, P., La Corte, V., Arcangeli, M., Zalla, T., Lemaire, S., Dokic, J., Nicolas, S., & Piolino, P. (2019). [Phenomenal, Bodily and Brain Correlates of Fictional Reappraisal as an Implicit Emotion Regulation Strategy](https://dominiquemakowski.github.io/publication/makowski2019phenomenal/makowski2019phenomenal.pdf). *Cognitive, Affective, & Behavioral Neuroscience*, 19(4), 1-21.

**Makowski, D.**, Sperduti, M., Blondé, P., Nicolas, S., & Piolino, P. (2019). [The heart of cognitive control: Cardiac phase modulates processing speed and inhibition](https://dominiquemakowski.github.io/publication/makowski2019heart/makowski2019heart.pdf). *Psychophysiology, 57*(3).

**Makowski, D.**\*, Sperduti, M.\*, Nicolas, S. & Piolino, P. (2017). ["*Being there*" and remembering it: Presence improves Memory Encoding](https://dominiquemakowski.github.io/publication/makowski2017being/makowski2017being.pdf). *Consciousness & Cognition, 53*, 194–202.

Sperduti, M.\*, **Makowski, D.**\*, Arcangeli, M., Wantzen, P., Zalla, T., Lemaire, S., Dokic, J., Pelletier, J. & Piolino, P. (2017). [The Distinctive Role of Executive Functions in Implicit Emotion Regulation](https://dominiquemakowski.github.io/publication/sperduti2017distinctive/sperduti2017distinctive.pdf). *Acta Psychologica, 173*, 13-20.

**Makowski, D.**, Ben-Shachar, M., & Lüdecke, D. (2019). [bayestestR: Describing effects and their uncertainty, existence and significance within the Bayesian framework](https://joss.theoj.org/papers/10.21105/joss.01541). *Journal of Open Source Software, 4*(40), 1541.

\normalsize

# Publication List

```{r, child=c('publications.Rmd')}
```
